# Multi-valley crossing results

Here we present the results for the **best performances** and **best gene value** generated by each selection scheme replicate on the multi-valley crossing diagnostic.
Best performance found refers to the largest average trait score found in a given population.
Best gene value refers to maximum gene value found in the population; this gives us a range of values in [0.0, 100.0].

## Analysis dependencies

```{r mvc-libs, message=FALSE}
library(ggplot2)
library(cowplot)
library(dplyr)
library(PupillometryR)
```

## Setup

These analyses were conducted in the following computing environment:

```{r mvc-ver}
print(version)
```

## Performance

Performance analysis.

### Over time

Best performance in a population over time.

```{r mvc-per-ot, warning=FALSE}
multivalley_crossing = filter(cc_over_time, diagnostic == 'multivalley_crossing')
lines = multivalley_crossing %>%
        group_by(`Selection\nScheme`, gen) %>%
          dplyr::summarise(
            min = min(pop_fit_max),
            mean = mean(pop_fit_max),
            max = max(pop_fit_max)
          )
points = filter(lines, gen %% 2000 == 0 & gen != 0)

ot = ggplot(lines, aes(x=gen, y=mean / TRAITS, group = `Selection\nScheme`, fill =`Selection\nScheme`, color = `Selection\nScheme`, shape = `Selection\nScheme`)) +
  geom_ribbon(aes(ymin = min / TRAITS, ymax = max / TRAITS), alpha = 0.1) +
  geom_line(size = 0.5) +
  geom_point(data = points, size = 1.5, stroke = 2.0, alpha = 1.0) +
  scale_y_continuous(
    name="Average trait score",
    limits=c(-1, 51),
    breaks=seq(0,50, 10),
    labels=c("0", "10", "20", "30", "40", "50")
  ) +
  scale_x_continuous(
    name="Generations",
    limits=c(0, 50000),
    breaks=c(0, 10000, 20000, 30000, 40000, 50000),
    labels=c("0e+6", "1e+6", "2e+6", "3e+6", "4e+6", "5e+6")

  ) +
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette) +
  scale_fill_manual(values = cb_palette) +
  ggtitle("Best performance over time") +
  p_theme+
    guides(
    shape=guide_legend(ncol=2, title.position = "bottom"),
    color=guide_legend(ncol=2, title.position = "bottom"),
    fill=guide_legend(ncol=2, title.position = "bottom")
  ) +
  theme(
    legend.position = "bottom",
    legend.box="verticle",
    legend.justification="center",
    legend.title=element_blank()
  )

ot
```

```{r mvc-per-lgd, echo = FALSE}
legend <- cowplot::get_legend(
  ot +
    guides(
      shape=guide_legend(ncol=2, title.position = "bottom"),
      color=guide_legend(ncol=2, title.position = "bottom"),
      fill=guide_legend(ncol=2, title.position = "bottom")
    ) +
    theme(
      legend.position = "top",
      legend.box="verticle",
      legend.justification="center",
      legend.title=element_blank()
    )
)
```

### Best performance throughout

Best performance throughout 50,000 generations.

```{r mvc-per-bst}
best = filter(cc_best, col == 'pop_fit_max' & diagnostic == 'multivalley_crossing')
plot = ggplot(best, aes(x = acron, y = val / TRAITS, color = acron, fill = acron, shape = acron)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), scale = 'width', alpha = 0.2) +
  geom_point(position = position_jitter(width = .1), size = 1.5, alpha = 1.0) +
  geom_boxplot(color = 'black', width = .2, outlier.shape = NA, alpha = 0.0) +
  scale_y_continuous(
    name="Average trait score",
    limits=c(-1, 51),
    breaks=seq(0,50, 10),
    labels=c("0", "10", "20", "30", "40", "50")
  ) +
  scale_x_discrete(
    name="Scheme"
  )+
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette) +
  scale_fill_manual(values = cb_palette) +
  p_theme

plot_grid(
  plot +
    ggtitle("Best performance throughout") +
    theme(legend.position="none"),
  legend,
  nrow=2,
  rel_heights = c(2,.55),
  label_size = TSIZE
)
```

#### Stats

Summary statistics for the best performance throughout 50,000 generations.

```{r mvc-per-bst-sum}
best$acron <- factor(best$acron, levels = c('pfs','gfs','nov','tor','tru','nds','ran','lex'))
group_by(best, acron) %>%
  dplyr::summarise(
    count = n(),
    na_cnt = sum(is.na(val)),
    min = min(val, na.rm = TRUE),
    median = median(val, na.rm = TRUE),
    mean = mean(val, na.rm = TRUE),
    max = max(val, na.rm = TRUE),
    IQR = IQR(val, na.rm = TRUE)
  )
```

Kruskal–Wallis test provides evidence of difference among best performances throughout 50,000 generations.

```{r mvc-per-bst-kru}
kruskal.test(val ~ acron,data = best)
```

Results for post-hoc Wilcoxon rank-sum test with a Bonferroni correction on best performance throughout 50,000 generations.

```{r mvc-per-bst-wil}
pairwise.wilcox.test(x = best$val, g = best$acron, p.adjust.method = "bonferroni",
                     paired = FALSE, conf.int = FALSE, alternative = 'l')
```

### End of 50,000 generations

Best performance in the population at the end of 50,000 generations.

```{r mvc-per-end}
end = filter(cc_end, diagnostic == 'multivalley_crossing')
plot = ggplot(end, aes(x = acron, y = pop_fit_max / TRAITS, color = acron, fill = acron, shape = acron)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), scale = 'width', alpha = 0.2) +
  geom_point(position = position_jitter(width = .1), size = 1.5, alpha = 1.0) +
  geom_boxplot(color = 'black', width = .2, outlier.shape = NA, alpha = 0.0) +
  scale_y_continuous(
    name="Average trait score",
    limits=c(-1, 51),
    breaks=seq(0,50, 10),
    labels=c("0", "10", "20", "30", "40", "50")
  ) +
  scale_x_discrete(
    name="Scheme"
  )+
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette) +
  scale_fill_manual(values = cb_palette) +
  p_theme

plot_grid(
  plot +
    ggtitle("Final performance") +
    theme(legend.position="none"),
  legend,
  nrow=2,
  rel_heights = c(2,.55),
  label_size = TSIZE
)
```

#### Stats

Summary statistics for best performance in the population at the end of 50,000 generations.

```{r mvc-per-end-sum}
end$acron <- factor(end$acron, levels = c('pfs','gfs','nov','tor','tru','nds','ran','lex'))
group_by(end, acron) %>%
  dplyr::summarise(
    count = n(),
    na_cnt = sum(is.na(pop_fit_max)),
    min = min(pop_fit_max, na.rm = TRUE),
    median = median(pop_fit_max, na.rm = TRUE),
    mean = mean(pop_fit_max, na.rm = TRUE),
    max = max(pop_fit_max, na.rm = TRUE),
    IQR = IQR(pop_fit_max, na.rm = TRUE)
  )
```

Kruskal–Wallis test provides evidence of difference among best performances in the population at the end of 50,000 generations.
```{r mvc-per-end-kru}
kruskal.test(pop_fit_max ~ acron,data = end)
```

Results for post-hoc Wilcoxon rank-sum test with a Bonferroni correction on best performances in the population at the end of 50,000 generations.

```{r mvc-per-end-wil}
pairwise.wilcox.test(x = end$pop_fit_max, g = end$acron, p.adjust.method = "bonferroni",
                     paired = FALSE, conf.int = FALSE, alternative = 'l')
```

## Best gene value

Best gene value analysis.

### Over time gene value

Best gene value over time.

```{r mvc-gne-ot, warning=FALSE}
multivalley_crossing = filter(cc_over_time, diagnostic == 'multivalley_crossing')

lines = multivalley_crossing %>%
        group_by(`Selection\nScheme`, gen) %>%
          dplyr::summarise(
            min = min(pop_max_gene),
            mean = mean(pop_max_gene),
            max = max(pop_max_gene)
          )
points = filter(lines, gen %% 2000 == 0 & gen != 0)

ot = ggplot(lines, aes(x=gen, y=mean, group = `Selection\nScheme`, fill =`Selection\nScheme`, color = `Selection\nScheme`, shape = `Selection\nScheme`)) +
  geom_ribbon(aes(ymin = min, ymax = max), alpha = 0.1) +
  geom_line(size = 0.5) +
  geom_point(data = points, size = 1.5, stroke = 2.0, alpha = 1.0) +
  scale_y_continuous(
    name="Max gene value",
    limits=c(-1, 101),
    breaks=seq(0,100, 20),
    labels=c("0", "20", "40", "60", "80", "100")
  ) +
  scale_x_continuous(
    name="Generations",
    limits=c(0, 50000),
    breaks=c(0, 10000, 20000, 30000, 40000, 50000),
    labels=c("0e+6", "1e+6", "2e+6", "3e+6", "4e+6", "5e+6")

  ) +
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette) +
  scale_fill_manual(values = cb_palette) +
  ggtitle("Best gene value over time") +
  p_theme+
    guides(
    shape=guide_legend(ncol=2, title.position = "bottom"),
    color=guide_legend(ncol=2, title.position = "bottom"),
    fill=guide_legend(ncol=2, title.position = "bottom")
  ) +
  theme(
    legend.position = "bottom",
    legend.box="verticle",
    legend.justification="center",
    legend.title=element_blank()
  )

ot
```

### Best gene value throughout

Best gene value throughout 50,000 generations.

```{r mvc-gne-bst}
best = filter(cc_best, col == 'pop_max_gene' & diagnostic == 'multivalley_crossing')
plot = ggplot(best, aes(x = acron, y = val, color = acron, fill = acron, shape = acron)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), scale = 'width', alpha = 0.2) +
  geom_point(position = position_jitter(width = .1), size = 1.5, alpha = 1.0) +
  geom_boxplot(color = 'black', width = .2, outlier.shape = NA, alpha = 0.0) +
  scale_y_continuous(
    name="Max gene value",
    limits=c(-1, 101),
    breaks=seq(0,100, 20),
    labels=c("0", "20", "40", "60", "80", "100")
  ) +
  scale_x_discrete(
    name="Scheme"
  )+
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette) +
  scale_fill_manual(values = cb_palette) +
  p_theme

plot_grid(
  plot +
    ggtitle("Best gene value throughout") +
    theme(legend.position="none"),
  legend,
  nrow=2,
  rel_heights = c(2,.55),
  label_size = TSIZE
)
```

#### Stats

Summary statistics for the best gene value throughout 50,000 generations.

```{r mvc-gne-bst-sum}
best$acron <- factor(best$acron, levels = c('pfs','gfs','nds','nov','ran','lex','tor','tru'))
group_by(best, acron) %>%
  dplyr::summarise(
    count = n(),
    na_cnt = sum(is.na(val)),
    min = min(val, na.rm = TRUE),
    median = median(val, na.rm = TRUE),
    mean = mean(val, na.rm = TRUE),
    max = max(val, na.rm = TRUE),
    IQR = IQR(val, na.rm = TRUE)
  )
```

Kruskal–Wallis test provides evidence of difference among best gene value throughout 50,000 generations.

```{r mvc-gne-bst-kru}
kruskal.test(val ~ acron,data = best)
```

Results for post-hoc Wilcoxon rank-sum test with a Bonferroni correction on best gene value throughout 50,000 generations.

```{r mvc-gne-bst-wil}
pairwise.wilcox.test(x = best$val, g = best$acron, p.adjust.method = "bonferroni",
                     paired = FALSE, conf.int = FALSE, alternative = 'l')
```


### End of 50,000 generations

Best gene value in the population at the end of 50,000 generations.

```{r mvc-gne-end}
end = filter(cc_end, diagnostic == 'multivalley_crossing')
end_p = ggplot(end, aes(x = acron, y = pop_max_gene, color = acron, fill = acron, shape = acron)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), scale = 'width', alpha = 0.2) +
  geom_point(position = position_jitter(width = .1), size = 1.5, alpha = 1.0) +
  geom_boxplot(color = 'black', width = .2, outlier.shape = NA, alpha = 0.0) +
  scale_y_continuous(
    name="Max gene value",
    limits=c(-1, 101),
    breaks=seq(0,100, 20),
    labels=c("0", "20", "40", "60", "80", "100")
  ) +
  scale_x_discrete(
    name="Scheme"
  )+
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette) +
  scale_fill_manual(values = cb_palette) +
  p_theme

plot_grid(
  end_p +
    ggtitle("Final gene value") +
    theme(legend.position="none"),
  legend,
  nrow=2,
  rel_heights = c(2,.55),
  label_size = TSIZE
)
```

#### Stats

Summary statistics for best gene values in the population at the end of 50,000 generations.

```{r mvc-gne-end-sum}
end$acron <- factor(end$acron, levels = c('pfs','gfs','nds','nov','ran','lex','tor','tru'))
group_by(end, acron) %>%
  dplyr::summarise(
    count = n(),
    na_cnt = sum(is.na(pop_max_gene)),
    min = min(pop_max_gene, na.rm = TRUE),
    median = median(pop_max_gene, na.rm = TRUE),
    mean = mean(pop_max_gene, na.rm = TRUE),
    max = max(pop_max_gene, na.rm = TRUE),
    IQR = IQR(pop_max_gene, na.rm = TRUE)
  )
```

Kruskal–Wallis test provides evidence of difference among best gene values in the population at the end of 50,000 generations.
```{r mvc-gne-end-kru}
kruskal.test(pop_max_gene ~ acron,data = end)
```

Results for post-hoc Wilcoxon rank-sum test with a Bonferroni correction on best gene values in the population at the end of 50,000 generations.

```{r mvc-gne-end-wil}
pairwise.wilcox.test(x = end$pop_max_gene, g = end$acron, p.adjust.method = "bonferroni",
                     paired = FALSE, conf.int = FALSE, alternative = 'l')
```