# Multi-path mpeloration results

Here we present the results for the **best performances** and **activation gene coverage** generated by each selection scheme replicate on the multi-path mpeloration diagnostic.
Best performance found refers to the largest average trait score found in a given population.
Note that activation gene coverage values are gathered at the population-level.
Activation gene coverage refers to the count of unique activation genes in a given population; this gives us a range of integers between 0 and 100.

## Analysis dependencies

```{r mpe-libs, message=FALSE}
library(ggplot2)
library(cowplot)
library(dplyr)
library(PupillometryR)
library(sdamr)
```

## Performance

Performance analysis.

### Over time

Best performance in a population over time.

```{r mpe-per-ot, warning=FALSE}
# data for lines and shading on plots
lines = filter(cc_over_time, diagnostic == 'multipath_mpeloration') %>%
  group_by(`Selection\nScheme`, gen) %>%
  dplyr::summarise(
    min = min(pop_fit_max) / DIMENSIONALITY,
    mean = mean(pop_fit_max) / DIMENSIONALITY,
    max = max(pop_fit_max) / DIMENSIONALITY
  )
ggplot(lines, aes(x=gen, y=mean, group = `Selection\nScheme`, fill =`Selection\nScheme`, color = `Selection\nScheme`, shape = `Selection\nScheme`)) +
  geom_ribbon(aes(ymin = min, ymax = max), alpha = 0.1) +
  geom_line(size = 0.5) +
  geom_point(data = filter(lines, gen %% 2000 == 0 & gen != 0), size = 1.5, stroke = 2.0, alpha = 1.0) +
  scale_y_continuous(
    name="Average trait score",
    limits=c(0, 100),
    breaks=seq(0,100, 20),
    labels=c("0", "20", "40", "60", "80", "100")
  ) +
  scale_x_continuous(
    name="Generations",
    limits=c(0, 50000),
    breaks=c(0, 10000, 20000, 30000, 40000, 50000),
    labels=c("0e+4", "1e+4", "2e+4", "3e+4", "4e+4", "5e+4")

  ) +
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette) +
  scale_fill_manual(values = cb_palette) +
  ggtitle('Performance over time')+
  p_theme + theme(legend.title=element_blank(),legend.text=element_text(size=11)) +
  guides(
    shape=guide_legend(ncol=2, title.position = "bottom"),
    color=guide_legend(ncol=2, title.position = "bottom"),
    fill=guide_legend(ncol=2, title.position = "bottom")
  )
```

### Best performance throughout

Best performance throughout 50,000 generations.

```{r mpe-per-bst}
### best performance throughout
filter(cc_best, col == 'pop_fit_max' & diagnostic == 'multipath_mpeloration') %>%
  ggplot(., aes(x = acron, y = val / DIMENSIONALITY, color = acron, fill = acron, shape = acron)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), scale = 'width', alpha = 0.2) +
  geom_point(position = position_jitter(width = .1), size = 1.5, alpha = 1.0) +
  geom_boxplot(color = 'black', width = .2, outlier.shape = NA, alpha = 0.0) +
  guides(fill = "none",color = 'none', shape = 'none') +
  scale_y_continuous(
    name="Average trait score",
    limits=c(-1, 101),
    breaks=seq(0,100, 20),
    labels=c("0", "20", "40", "60", "80", "100")
  ) +
  scale_x_discrete(
    name="Scheme"
  )+
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette, ) +
  scale_fill_manual(values = cb_palette) +
  ggtitle('Best performance throughout')+
  p_theme + theme(legend.title=element_blank()) +
  guides(
    shape=guide_legend(nrow=2, title.position = "bottom"),
    color=guide_legend(nrow=2, title.position = "bottom"),
    fill=guide_legend(nrow=2, title.position = "bottom")
  )
```

#### Stats

Summary statistics for the best performance.

```{r mpe-per-bst-sum}
### best performance throughout
performance = filter(cc_best, col == 'pop_fit_max' & diagnostic == 'multipath_mpeloration')
performance$acron = factor(performance$acron, levels = c('lex','tor','tru','nds','gfs','pfs','nov','ran'))
performance %>%
  group_by(acron) %>%
  dplyr::summarise(
    count = n(),
    na_cnt = sum(is.na(val)),
    min = min(val / DIMENSIONALITY, na.rm = TRUE),
    median = median(val / DIMENSIONALITY, na.rm = TRUE),
    mean = mean(val / DIMENSIONALITY, na.rm = TRUE),
    max = max(val / DIMENSIONALITY, na.rm = TRUE),
    IQR = IQR(val / DIMENSIONALITY, na.rm = TRUE)
  )
```

Kruskal–Wallis test provides evidence of difference among best performances.

```{r mpe-per-bst-kru}
kruskal.test(val ~ acron, data = performance)
```

Results for post-hoc Wilcoxon rank-sum test with a Bonferroni correction on best performance.

```{r mpe-per-bst-wil}
pairwise.wilcox.test(x = performance$val, g = performance$acron, p.adjust.method = "bonferroni",
                     paired = FALSE, conf.int = FALSE, alternative = 'l')
```

### End of 50,000 generations

Best performance in the population at the end of 50,000 generations.

```{r mpe-per-end}
# end of run
filter(cc_over_time, diagnostic == 'multipath_mpeloration' & gen == 50000) %>%
  ggplot(., aes(x = acron, y = pop_fit_max / DIMENSIONALITY, color = acron, fill = acron, shape = acron)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), scale = 'width', alpha = 0.2) +
  geom_point(position = position_jitter(width = .1), size = 1.5, alpha = 1.0) +
  geom_boxplot(color = 'black', width = .2, outlier.shape = NA, alpha = 0.0) +
  guides(fill = "none",color = 'none', shape = 'none') +
  scale_y_continuous(
    name="Coverage",
    limits=c(0, 100),
    breaks=seq(0,100, 20),
    labels=c("0", "20", "40", "60", "80", "100")
  ) +
  scale_x_discrete(
    name="Scheme"
  )+
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette, ) +
  scale_fill_manual(values = cb_palette) +
  ggtitle('Final performance')+
  p_theme + theme(legend.title=element_blank()) +
  guides(
    shape=guide_legend(nrow=2, title.position = "bottom"),
    color=guide_legend(nrow=2, title.position = "bottom"),
    fill=guide_legend(nrow=2, title.position = "bottom")
  )
```

#### Stats

Summary statistics for best performance in the final population.

```{r mpe-per-end-sum}
# end of run
performance = filter(cc_over_time, diagnostic == 'multipath_mpeloration' & gen == 50000)
performance$acron = factor(performance$acron, levels = c('lex','tor','tru','nds','gfs','pfs','nov','ran'))
performance %>%
  group_by(acron) %>%
  dplyr::summarise(
    count = n(),
    na_cnt = sum(is.na(pop_fit_max / DIMENSIONALITY)),
    min = min(pop_fit_max / DIMENSIONALITY, na.rm = TRUE),
    median = median(pop_fit_max / DIMENSIONALITY, na.rm = TRUE),
    mean = mean(pop_fit_max / DIMENSIONALITY, na.rm = TRUE),
    max = max(pop_fit_max / DIMENSIONALITY, na.rm = TRUE),
    IQR = IQR(pop_fit_max / DIMENSIONALITY, na.rm = TRUE)
  )
```

Kruskal–Wallis test provides evidence of difference among best performance in the final population.
```{r mpe-per-end-kru}
kruskal.test(pop_fit_max ~ acron, data = performance)
```

Results for post-hoc Wilcoxon rank-sum test with a Bonferroni correction on best performance in the final population.

```{r mpe-per-end-wil}
pairwise.wilcox.test(x = performance$pop_fit_max, g = performance$acron, p.adjust.method = "bonferroni",
                     paired = FALSE, conf.int = FALSE, alternative = 'l')
```

## Activation gene coverage

Activation gene coverage analysis.

### Over time coverage

Activation gene coverage over time.

```{r mpe-act-ot, warning=FALSE}
# data for lines and shading on plots
lines = filter(cc_over_time, diagnostic == 'multipath_mpeloration') %>%
  group_by(`Selection\nScheme`, gen) %>%
  dplyr::summarise(
    min = min(uni_str_pos),
    mean = mean(uni_str_pos),
    max = max(uni_str_pos)
  )
ggplot(lines, aes(x=gen, y=mean, group = `Selection\nScheme`, fill =`Selection\nScheme`, color = `Selection\nScheme`, shape = `Selection\nScheme`)) +
  geom_ribbon(aes(ymin = min, ymax = max), alpha = 0.1) +
  geom_line(size = 0.5) +
  geom_point(data = filter(lines, gen %% 2000 == 0 & gen != 0), size = 1.5, stroke = 2.0, alpha = 1.0) +
  scale_y_continuous(
    name="Coverage",
    limits=c(0, 100),
    breaks=seq(0,100, 20),
    labels=c("0", "20", "40", "60", "80", "100")
  ) +
  scale_x_continuous(
    name="Generations",
    limits=c(0, 50000),
    breaks=c(0, 10000, 20000, 30000, 40000, 50000),
    labels=c("0e+4", "1e+4", "2e+4", "3e+4", "4e+4", "5e+4")
  ) +
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette) +
  scale_fill_manual(values = cb_palette) +
  ggtitle('Activation gene coverage over time')+
  p_theme + theme(legend.title=element_blank(),legend.text=element_text(size=11)) +
  guides(
    shape=guide_legend(ncol=2, title.position = "bottom"),
    color=guide_legend(ncol=2, title.position = "bottom"),
    fill=guide_legend(ncol=2, title.position = "bottom")
  )
```

### End of 50,000 generations

Activation gene coverage in the population at the end of 50,000 generations.

```{r mpe-act-end}
# end of run
filter(cc_over_time, diagnostic == 'multipath_mpeloration' & gen == 50000) %>%
  ggplot(., aes(x = acron, y = uni_str_pos, color = acron, fill = acron, shape = acron)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), scale = 'width', alpha = 0.2) +
  geom_point(position = position_jitter(width = .1), size = 1.5, alpha = 1.0) +
  geom_boxplot(color = 'black', width = .2, outlier.shape = NA, alpha = 0.0) +
  guides(fill = "none",color = 'none', shape = 'none') +
  scale_y_continuous(
    name="Coverage",
    limits=c(0, 100),
    breaks=seq(0,100, 20),
    labels=c("0", "20", "40", "60", "80", "100")
  ) +
  scale_x_discrete(
    name="Scheme"
  )+
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette, ) +
  scale_fill_manual(values = cb_palette) +
  ggtitle('Final activation gene coverage')+
  p_theme + theme(legend.title=element_blank()) +
  guides(
    shape=guide_legend(nrow=2, title.position = "bottom"),
    color=guide_legend(nrow=2, title.position = "bottom"),
    fill=guide_legend(nrow=2, title.position = "bottom")
  )
```

#### Stats

Summary statistics for activation gene coverage in the final population.

```{r mpe-act-end-sum}
# end of run
coverage = filter(cc_over_time, diagnostic == 'multipath_mpeloration' & gen == 50000)
coverage$acron = factor(coverage$acron, levels = c('nov','lex','nds','gfs','pfs','tor','tru','ran'))
coverage %>%
  group_by(acron) %>%
  dplyr::summarise(
    count = n(),
    na_cnt = sum(is.na(uni_str_pos)),
    min = min(uni_str_pos, na.rm = TRUE),
    median = median(uni_str_pos, na.rm = TRUE),
    mean = mean(uni_str_pos, na.rm = TRUE),
    max = max(uni_str_pos, na.rm = TRUE),
    IQR = IQR(uni_str_pos, na.rm = TRUE)
  )
```

Kruskal–Wallis test provides evidence of difference among activation gene coverage in the final population.
```{r mpe-act-end-kru}
kruskal.test(uni_str_pos ~ acron, data = coverage)
```

Results for post-hoc Wilcoxon rank-sum test with a Bonferroni correction on activation gene coverage in the final population.

```{r mpe-act-end-wil}
pairwise.wilcox.test(x = coverage$uni_str_pos, g = coverage$acron, p.adjust.method = "bonferroni",
                     paired = FALSE, conf.int = FALSE, alternative = 'l')
```



## Multi-valley crossing results

### Performance

Performance analysis.

#### Performance over time

Best performance in a population over time.

```{r mpe-mvc-per-ot, warning=FALSE}
# data for lines and shading on plots
lines = filter(cc_over_time_mvc, diagnostic == 'multipath_exploration') %>%
  group_by(`Selection\nScheme`, gen) %>%
  dplyr::summarise(
    min = min(pop_fit_max) / DIMENSIONALITY,
    mean = mean(pop_fit_max) / DIMENSIONALITY,
    max = max(pop_fit_max) / DIMENSIONALITY
  )
ggplot(lines, aes(x=gen, y=mean, group = `Selection\nScheme`, fill =`Selection\nScheme`, color = `Selection\nScheme`, shape = `Selection\nScheme`)) +
  geom_ribbon(aes(ymin = min, ymax = max), alpha = 0.1) +
  geom_line(size = 0.5) +
  geom_point(data = filter(lines, gen %% 2000 == 0 & gen != 0), size = 1.5, stroke = 2.0, alpha = 1.0) +
  scale_y_continuous(
    name="Average trait score",
    limits=c(0, 15),
    breaks=seq(0,15, 5),
    labels=c("0", "5", "10", "15")
  ) +
  scale_x_continuous(
    name="Generations",
    limits=c(0, 50000),
    breaks=c(0, 10000, 20000, 30000, 40000, 50000),
    labels=c("0e+4", "1e+4", "2e+4", "3e+4", "4e+4", "5e+4")

  ) +
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette) +
  scale_fill_manual(values = cb_palette) +
  ggtitle('Performance over time')+
  p_theme + theme(legend.title=element_blank(),legend.text=element_text(size=11)) +
  guides(
    shape=guide_legend(ncol=2, title.position = "bottom"),
    color=guide_legend(ncol=2, title.position = "bottom"),
    fill=guide_legend(ncol=2, title.position = "bottom")
  )
```

#### Best performance throughout

Best performance found throughout 50,000 generations.

```{r mpe-mvc-per-bst}
### best performance throughout
filter(cc_best_mvc, col == 'pop_fit_max' & diagnostic == 'multipath_exploration') %>%
  ggplot(., aes(x = acron, y = val / DIMENSIONALITY, color = acron, fill = acron, shape = acron)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), scale = 'width', alpha = 0.2) +
  geom_point(position = position_jitter(width = .1), size = 1.5, alpha = 1.0) +
  geom_boxplot(color = 'black', width = .2, outlier.shape = NA, alpha = 0.0) +
  guides(fill = "none",color = 'none', shape = 'none') +
  scale_y_continuous(
    name="Average trait score",
    limits=c(0, 15),
    breaks=seq(0,15, 5),
    labels=c("0", "5", "10", "15")
  ) +
  scale_x_discrete(
    name="Scheme"
  )+
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette, ) +
  scale_fill_manual(values = cb_palette) +
  ggtitle('Best performance throughout')+
  p_theme + theme(legend.title=element_blank()) +
  guides(
    shape=guide_legend(nrow=2, title.position = "bottom"),
    color=guide_legend(nrow=2, title.position = "bottom"),
    fill=guide_legend(nrow=2, title.position = "bottom")
  )
```

##### Stats

Summary statistics for the performance of the best performance.

```{r mpe-mvc-per-bst-sum}
### best performance throughout
performance = filter(cc_best_mvc, col == 'pop_fit_max' & diagnostic == 'multipath_exploration')
performance$acron = factor(performance$acron, levels = c('gfs','pfs','tor','tru','nov','lex','nds','ran'))
performance %>%
  group_by(acron) %>%
  dplyr::summarise(
    count = n(),
    na_cnt = sum(is.na(val)),
    min = min(val / DIMENSIONALITY, na.rm = TRUE),
    median = median(val / DIMENSIONALITY, na.rm = TRUE),
    mean = mean(val / DIMENSIONALITY, na.rm = TRUE),
    max = max(val / DIMENSIONALITY, na.rm = TRUE),
    IQR = IQR(val / DIMENSIONALITY, na.rm = TRUE)
  )
```

Kruskal–Wallis test provides evidence of statistical differences.

```{r mpe-mvc-per-bst-kru}
kruskal.test(val ~ acron, data = performance)
```

Results for post-hoc Wilcoxon rank-sum test with a Bonferroni correction.

```{r mpe-mvc-per-bst-wil}
pairwise.wilcox.test(x = performance$val, g = performance$acron, p.adjust.method = "bonferroni",
                     paired = FALSE, conf.int = FALSE, alternative = 'l')
```

#### Performance comparison

Best performances in the population at 40,000 and 50,000 generations.

```{r mpe-mvc-lgd, echo = FALSE}
dummy_df = filter(filter(cc_over_time_mvc, diagnostic == 'multipath_exploration' & (gen == 50000 | gen == 40000) & acron != 'ran'))
dummy_df$Generation <- factor(dummy_df$gen)
p = ggplot(dummy_df, aes(x=gen, y=pop_fit_max / DIMENSIONALITY, group = acron, fill = acron, color = Generation, shape = Generation)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), scale = 'width', alpha = 0.2) +
  geom_point(position = position_jitter(width = .03), size = 2, alpha = 1.0) +
  geom_boxplot(position = position_nudge(x = .13, y = 0), lwd = 1, width = .1, outlier.shape = NA, alpha = 0.0) +
  scale_shape_manual(values=c(0,1))+
  scale_colour_manual(values = mvc_col)+
  scale_fill_manual(values = cb_palette) + p_theme +
  guides(
    shape=guide_legend(ncol=2, title.position = "bottom"),
    color=guide_legend(ncol=2, title.position = "bottom"),
    fill='none')

legend <- cowplot::get_legend(
  p +
    guides(
      shape=guide_legend(ncol=2, title.position = "left"),
      color=guide_legend(ncol=2, title.position = "left"),
      fill='none'
    ) +
    theme(
      legend.position = "top",
      legend.box="verticle",
      legend.justification="center"
    )
)
rm(dummy_df, p)
```

```{r mpe-mvc-per-sli, warning=FALSE}
# 80% and final generation comparison
end = filter(cc_over_time_mvc, diagnostic == 'multipath_exploration' & gen == 50000 & acron != 'ran')
end$Generation <- factor(end$gen)

mid = filter(cc_over_time_mvc, diagnostic == 'multipath_exploration' & gen == 40000 & acron != 'ran')
mid$Generation <- factor(mid$gen)

mvc_p = ggplot(mid, aes(x = acron, y=pop_fit_max / DIMENSIONALITY, group = acron, shape = Generation)) +
  geom_point(col = mvc_col[1] , position = position_jitternudge(jitter.width = .03, nudge.x = -0.05), size = 2, alpha = 1.0) +
  geom_boxplot(position = position_nudge(x = -.15, y = 0), lwd = 0.7, col = mvc_col[1], fill = mvc_col[1], width = .1, outlier.shape = NA, alpha = 0.0) +

  geom_point(data = end, aes(x = acron, y=pop_fit_max / DIMENSIONALITY), col = mvc_col[2], position = position_jitternudge(jitter.width = .03, nudge.x = 0.05), size = 2, alpha = 1.0) +
  geom_boxplot(data = end, aes(x = acron, y=pop_fit_max / DIMENSIONALITY), position = position_nudge(x = .15, y = 0), lwd = 0.7, col = mvc_col[2], fill = mvc_col[2], width = .1, outlier.shape = NA, alpha = 0.0) +

  scale_y_continuous(
    name="Average trait score",
    limits=c(0, 15),
    breaks=seq(0,15, 5),
    labels=c("0", "5", "10", "15")
  ) +
  scale_x_discrete(
    name="Scheme"
  )+
  scale_shape_manual(values=c(0,1))+
  scale_colour_manual(values = c(mvc_col[1],mvc_col[2])) +
  p_theme

plot_grid(
  mvc_p +
    ggtitle("Performance comparisons") +
    theme(legend.position="none"),
  legend,
  nrow=2,
  rel_heights = c(1,.05),
  label_size = TSIZE
)
```

##### Stats

Summary statistics for the performance of the best performance at 40,000 and 50,000 generations.

```{r mpe-mvc-per-sli-sum}
### performance comparisons and generation slices 40K & 50K
slices = filter(cc_over_time_mvc, diagnostic == 'multipath_exploration' & (gen == 50000 | gen == 40000) & acron != 'ran')
slices$Generation <- factor(slices$gen, levels = c(50000,40000))
slices$acron = factor(slices$acron, levels = c('gfs','pfs','tru','tor','nov', 'nds','lex', 'ran'))
slices %>%
  group_by(acron, Generation) %>%
  dplyr::summarise(
    count = n(),
    na_cnt = sum(is.na(pop_fit_max  / DIMENSIONALITY)),
    min = min(pop_fit_max  / DIMENSIONALITY, na.rm = TRUE),
    median = median(pop_fit_max  / DIMENSIONALITY, na.rm = TRUE),
    mean = mean(pop_fit_max  / DIMENSIONALITY, na.rm = TRUE),
    max = max(pop_fit_max  / DIMENSIONALITY, na.rm = TRUE),
    IQR = IQR(pop_fit_max  / DIMENSIONALITY, na.rm = TRUE)
  )
```

Truncation selection comparisons.
```{r mpe-mvc-tru-per-cmp}
wilcox.test(x = filter(slices, acron == 'tru' & Generation == 50000)$pop_fit_max,
            y = filter(slices, acron == 'tru' & Generation == 40000)$pop_fit_max,
            alternative = 't')
```

Tournament selection comparisons.
```{r mpe-mvc-tor-per-cmp}
wilcox.test(x = filter(slices, acron == 'tor' & Generation == 50000)$pop_fit_max,
            y = filter(slices, acron == 'tor' & Generation == 40000)$pop_fit_max,
            alternative = 't')
```

Lexicase selection comparisons.
```{r mpe-mvc-lex-per-cmp}
wilcox.test(x = filter(slices, acron == 'lex' & Generation == 50000)$pop_fit_max,
            y = filter(slices, acron == 'lex' & Generation == 40000)$pop_fit_max,
            alternative = 't')
```

Genotypic fitness sharing comparisons.
```{r mpe-mvc-gfs-per-cmp}
wilcox.test(x = filter(slices, acron == 'gfs' & Generation == 50000)$pop_fit_max,
            y = filter(slices, acron == 'gfs' & Generation == 40000)$pop_fit_max,
            alternative = 't')
```

Phenotypic fitness sharing comparisons.
```{r mpe-mvc-pfs-per-cmp}
wilcox.test(x = filter(slices, acron == 'pfs' & Generation == 50000)$pop_fit_max,
            y = filter(slices, acron == 'pfs' & Generation == 40000)$pop_fit_max,
            alternative = 't')
```

Nondominated sorting comparisons.
```{r mpe-mvc-nds-per-cmp}
wilcox.test(x = filter(slices, acron == 'nds' & Generation == 50000)$pop_fit_max,
            y = filter(slices, acron == 'nds' & Generation == 40000)$pop_fit_max,
            alternative = 't')
```

 Novelty search comparisons.
```{r mpe-mvc-nov-per-cmp}
wilcox.test(x = filter(slices, acron == 'nov' & Generation == 50000)$pop_fit_max,
            y = filter(slices, acron == 'nov' & Generation == 40000)$pop_fit_max,
            alternative = 't')
```

### Activation gene coverage

Activation gene coverage analysis.

#### Coverage over time

Activation gene coverage over time.

```{r mpe-mvc-act-ot, warning=FALSE}
# data for lines and shading on plots
lines = filter(cc_over_time_mvc, diagnostic == 'multipath_exploration') %>%
  group_by(`Selection\nScheme`, gen) %>%
  dplyr::summarise(
    min = min(uni_str_pos),
    mean = mean(uni_str_pos),
    max = max(uni_str_pos)
  )
ggplot(lines, aes(x=gen, y=mean, group = `Selection\nScheme`, fill =`Selection\nScheme`, color = `Selection\nScheme`, shape = `Selection\nScheme`)) +
  geom_ribbon(aes(ymin = min, ymax = max), alpha = 0.1) +
  geom_line(size = 0.5) +
  geom_point(data = filter(lines, gen %% 2000 == 0 & gen != 0), size = 1.5, stroke = 2.0, alpha = 1.0) +
  scale_y_continuous(
    name="Coverage",
    limits=c(0, 100),
    breaks=seq(0,100, 20),
    labels=c("0", "20", "40", "60", "80", "100")
  ) +
  scale_x_continuous(
    name="Generations",
    limits=c(0, 50000),
    breaks=c(0, 10000, 20000, 30000, 40000, 50000),
    labels=c("0e+4", "1e+4", "2e+4", "3e+4", "4e+4", "5e+4")
  ) +
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette) +
  scale_fill_manual(values = cb_palette) +
  ggtitle('Activation gene coverage over time')+
  p_theme + theme(legend.title=element_blank(),legend.text=element_text(size=11)) +
  guides(
    shape=guide_legend(ncol=2, title.position = "bottom"),
    color=guide_legend(ncol=2, title.position = "bottom"),
    fill=guide_legend(ncol=2, title.position = "bottom")
  )
```

#### Coverage comparison

Best activation gene coverage in the population at 40,000 and 50,000 generations.

```{r mpe-mvc-act-sli, warning=FALSE}
# 80% and final generation comparison
end = filter(cc_over_time_mvc, diagnostic == 'multipath_exploration' & gen == 50000 & acron != 'ran')
end$Generation <- factor(end$gen)

mid = filter(cc_over_time_mvc, diagnostic == 'multipath_exploration' & gen == 40000 & acron != 'ran')
mid$Generation <- factor(mid$gen)

mvc_p = ggplot(mid, aes(x = acron, y=uni_str_pos, group = acron, shape = Generation)) +
  geom_point(col = mvc_col[1] , position = position_jitternudge(jitter.width = .03, nudge.x = -0.05), size = 2, alpha = 1.0) +
  geom_boxplot(position = position_nudge(x = -.17, y = 0), lwd = 0.7, col = mvc_col[1], fill = mvc_col[1], width = .1, outlier.shape = NA, alpha = 0.0) +

  geom_point(data = end, aes(x = acron, y=uni_str_pos), col = mvc_col[2], position = position_jitternudge(jitter.width = .03, nudge.x = 0.05), size = 2, alpha = 1.0) +
  geom_boxplot(data = end, aes(x = acron, y=uni_str_pos), position = position_nudge(x = .17, y = 0), lwd = 0.7, col = mvc_col[2], fill = mvc_col[2], width = .1, outlier.shape = NA, alpha = 0.0) +

  scale_y_continuous(
    name="Coverage",
    limits=c(0, 100),
    breaks=seq(0,100, 20),
    labels=c("0", "20", "40", "60", "80", "100")
  ) +
  scale_x_discrete(
    name="Scheme"
  )+
  scale_shape_manual(values=c(0,1))+
  scale_colour_manual(values = c(mvc_col[1],mvc_col[2])) +
  p_theme

plot_grid(
  mvc_p +
    ggtitle("Activation gene coverage comparisons") +
    theme(legend.position="none"),
  legend,
  nrow=2,
  rel_heights = c(1,.05),
  label_size = TSIZE
)
```

#### Stats

Summary statistics for the activation gene coverage at 40,000 and 50,000 generations.

```{r mpe-mvc-act-sli-sum}
slices = filter(cc_over_time_mvc, diagnostic == 'multipath_exploration' & (gen == 50000 | gen == 40000) & acron != 'ran')
slices$Generation <- factor(slices$gen, levels = c(50000,40000))
slices$acron = factor(slices$acron, levels = c('nov','lex', 'nds','tru','tor','gfs','pfs','ran'))
slices %>%
  group_by(acron, Generation) %>%
  dplyr::summarise(
    count = n(),
    na_cnt = sum(is.na(uni_str_pos)),
    min = min(uni_str_pos, na.rm = TRUE),
    median = median(uni_str_pos, na.rm = TRUE),
    mean = mean(uni_str_pos, na.rm = TRUE),
    max = max(uni_str_pos, na.rm = TRUE),
    IQR = IQR(uni_str_pos, na.rm = TRUE)
  )
```

Truncation selection comparisons.
```{r mpe-mvc-tru-act-cmp}
wilcox.test(x = filter(slices, acron == 'tru' & Generation == 50000)$uni_str_pos,
            y = filter(slices, acron == 'tru' & Generation == 40000)$uni_str_pos,
            alternative = 't')
```

Tournament selection comparisons.
```{r mpe-mvc-tor-act-cmp}
wilcox.test(x = filter(slices, acron == 'tor' & Generation == 50000)$uni_str_pos,
            y = filter(slices, acron == 'tor' & Generation == 40000)$uni_str_pos,
            alternative = 't')
```

Lexicase selection comparisons.
```{r mpe-mvc-lex-act-cmp}
wilcox.test(x = filter(slices, acron == 'lex' & Generation == 50000)$uni_str_pos,
            y = filter(slices, acron == 'lex' & Generation == 40000)$uni_str_pos,
            alternative = 't')
```

Genotypic fitness sharing comparisons.
```{r mpe-mvc-gfs-act-cmp}
wilcox.test(x = filter(slices, acron == 'gfs' & Generation == 50000)$uni_str_pos,
            y = filter(slices, acron == 'gfs' & Generation == 40000)$uni_str_pos,
            alternative = 't')
```

Phenotypic fitness sharing comparisons.
```{r mpe-mvc-pfs-act-cmp}
wilcox.test(x = filter(slices, acron == 'pfs' & Generation == 50000)$uni_str_pos,
            y = filter(slices, acron == 'pfs' & Generation == 40000)$uni_str_pos,
            alternative = 't')
```

Nondominated sorting comparisons.
```{r mpe-mvc-nds-act-cmp}
wilcox.test(x = filter(slices, acron == 'nds' & Generation == 50000)$uni_str_pos,
            y = filter(slices, acron == 'nds' & Generation == 40000)$uni_str_pos,
            alternative = 't')
```

 Novelty search comparisons.
```{r mpe-mvc-nov-act-cmp}
wilcox.test(x = filter(slices, acron == 'nov' & Generation == 50000)$uni_str_pos,
            y = filter(slices, acron == 'nov' & Generation == 40000)$uni_str_pos,
            alternative = 't')
```