# Truncation selection

We present the results from our parameter sweeep on truncation selection.
50 replicates are conducted for each truncation size `T` parameter value explored.

```{r, message=FALSE}
library(ggplot2)
library(cowplot)
library(dplyr)
library(PupillometryR)
```

## Exploitation rate results

Here we present the results for **best performances** found by each truncation selection value replicate on the exploitation rate diagnostic.

### Performance over time

Performance over time.

```{r tru-exp-per, warning=FALSE}
lines = filter(tru_ot, diagnostic == 'exploitation_rate') %>%
        group_by(T, gen) %>%
          dplyr::summarise(
            min = min(pop_fit_max),
            mean = mean(pop_fit_max),
            max = max(pop_fit_max)
          )
ggplot(lines, aes(x=gen, y=mean / DIMENSIONALITY, group = T, fill = T, color = T, shape = T)) +
  geom_ribbon(aes(ymin = min / DIMENSIONALITY, ymax = max / DIMENSIONALITY), alpha = 0.1) +
  geom_line(size = 0.5) +
  geom_point(data = filter(lines, gen %% 2000 == 0 & gen != 0), size = 1.5, stroke = 2.0, alpha = 1.0) +
  scale_y_continuous(
    name="Average trait score"
  ) +
  scale_x_continuous(
    name="Generations",
    limits=c(0, 50000),
    breaks=c(0, 10000, 20000, 30000, 40000, 50000),
    labels=c("0e+4", "1e+4", "2e+4", "3e+4", "4e+4", "5e+4")

  ) +
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette) +
  scale_fill_manual(values = cb_palette) +
  ggtitle("Best performance over time") +
  p_theme
```

### Generation satisfactory solution found

The first Generations a satisfactory solution is found throughout the 50,000 generations.

```{r tru-exp-ssf}
filter(tru_ssf, Diagnostic == 'EXPLOITATION_RATE') %>%
ggplot(., aes(x = T, y = Generations, color = T, fill = T, shape = T)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), scale = 'width', alpha = 0.2) +
  geom_point(position = position_jitter(width = .1), size = 1.5, alpha = 1.0) +
  geom_boxplot(color = 'black', width = .2, outlier.shape = NA, alpha = 0.0) +
  scale_shape_manual(values=SHAPE)+
  scale_y_continuous(
    name="Generation",
    limits=c(0, 12000),
    breaks=c(0, 2000, 4000, 6000, 8000, 10000, 12000),
    labels=c("0e+4", "2e+4", "4e+4", "6e+4", "8e+4", "10e+4", "12e+4")
  ) +
  scale_x_discrete(
    name="T"
  ) +
  ggtitle("Generation satisfactory solution found") +
  scale_colour_manual(values = cb_palette) +
  scale_fill_manual(values = cb_palette) +
  p_theme
```

#### Stats

Summary statistics for the best performance found throughout 50,000 generations.

```{r tru-exp-ssf-sum}
ssf = filter(tru_ssf, Diagnostic == 'EXPLOITATION_RATE')
group_by(ssf, T) %>%
  dplyr::summarise(
    count = n(),
    na_cnt = sum(is.na(Generations)),
    min = min(Generations, na.rm = TRUE),
    median = median(Generations, na.rm = TRUE),
    mean = mean(Generations, na.rm = TRUE),
    max = max(Generations, na.rm = TRUE),
    IQR = IQR(Generations, na.rm = TRUE)
  )
```

Kruskal–Wallis test provides evidence of significant differences among the Generations a satisfactory solution is first found.

```{r tru-exp-ssf-kru}
kruskal.test(Generations ~ T,data = ssf)
```

Results for post-hoc Wilcoxon rank-sum test with a Bonferroni correction on the Generations a satisfactory solution is first found. .

```{r tru-exp-ssf-wal}
pairwise.wilcox.test(x = ssf$Generations, g = ssf$T , p.adjust.method = "bonferroni",
                     paired = FALSE, conf.int = FALSE, alternative = 'g')
```

### Multi-valley crossing

#### Performance over time

```{r tru-exp-mvc-per}
# data for lines and shading on plots
lines = filter(tru_ot_mvc, diagnostic == 'exploitation_rate') %>%
  group_by(T, gen) %>%
  dplyr::summarise(
    min = min(pop_fit_max) / DIMENSIONALITY,
    mean = mean(pop_fit_max) / DIMENSIONALITY,
    max = max(pop_fit_max) / DIMENSIONALITY
  )

ggplot(lines, aes(x=gen, y=mean, group = T, fill =T, color = T, shape = T)) +
  geom_ribbon(aes(ymin = min, ymax = max), alpha = 0.1) +
  geom_line(size = 0.5) +
  geom_point(data = filter(lines, gen %% 2000 == 0 & gen != 0), size = 1.5, stroke = 2.0, alpha = 1.0) +
  scale_y_continuous(
    name="Average trait score"
  ) +
  scale_x_continuous(
    name="Generations",
    limits=c(0, 50000),
    breaks=c(0, 10000, 20000, 30000, 40000, 50000),
    labels=c("0e+4", "1e+4", "2e+4", "3e+4", "4e+4", "5e+4")

  ) +
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette) +
  scale_fill_manual(values = cb_palette) +
  ggtitle('Performance over time')+
  p_theme +
  guides(
    shape=guide_legend(nrow=2, title.position = "left"),
    color=guide_legend(nrow=2, title.position = "left"),
    fill=guide_legend(nrow=2, title.position = "left")
  )

```

#### Performance comparison

Best performances in the population at 40,000 and 50,000 generations.

```{r tru-exp-mvc-per-sli, warning=FALSE}
# 80% and final generation comparison
end = filter(tru_ot_mvc, diagnostic == 'exploitation_rate' & gen == 50000 & T != 'ran')
end$Generation <- factor(end$gen)

mid = filter(tru_ot_mvc, diagnostic == 'exploitation_rate' & gen == 40000 & T != 'ran')
mid$Generation <- factor(mid$gen)

mvc_p = ggplot(mid, aes(x = T, y=pop_fit_max / DIMENSIONALITY, group = T, shape = Generation)) +
  geom_point(col = mvc_col[1] , position = position_jitternudge(jitter.width = .03, nudge.x = -0.05), size = 2, alpha = 1.0) +
  geom_boxplot(position = position_nudge(x = -.15, y = 0), lwd = 0.7, col = mvc_col[1], fill = mvc_col[1], width = .1, outlier.shape = NA, alpha = 0.0) +

  geom_point(data = end, aes(x = T, y=pop_fit_max / DIMENSIONALITY), col = mvc_col[2], position = position_jitternudge(jitter.width = .03, nudge.x = 0.05), size = 2, alpha = 1.0) +
  geom_boxplot(data = end, aes(x = T, y=pop_fit_max / DIMENSIONALITY), position = position_nudge(x = .15, y = 0), lwd = 0.7, col = mvc_col[2], fill = mvc_col[2], width = .1, outlier.shape = NA, alpha = 0.0) +

  scale_y_continuous(
    name="Average trait score"
  ) +
  scale_x_discrete(
    name="T"
  )+
  scale_shape_manual(values=c(0,1))+
  scale_colour_manual(values = c(mvc_col[1],mvc_col[2])) +
  p_theme

plot_grid(
  mvc_p +
    ggtitle("Performance comparisons") +
    theme(legend.position="none"),
  legend,
  nrow=2,
  rel_heights = c(1,.05),
  label_size = TSIZE
)
```

#### Stats

Summary statistics for the performance of the best performance at 40,000 and 50,000 generations.

```{r tru-exp-mvc-per-sli-sum}
slices = filter(tru_ot_mvc, diagnostic == 'exploitation_rate' & (gen == 50000 | gen == 40000))
slices$Generation <- factor(slices$gen, levels = c(50000,40000))
slices %>%
  group_by(T, Generation) %>%
  dplyr::summarise(
    count = n(),
    na_cnt = sum(is.na(pop_fit_max  / DIMENSIONALITY)),
    min = min(pop_fit_max  / DIMENSIONALITY, na.rm = TRUE),
    median = median(pop_fit_max  / DIMENSIONALITY, na.rm = TRUE),
    mean = mean(pop_fit_max  / DIMENSIONALITY, na.rm = TRUE),
    max = max(pop_fit_max  / DIMENSIONALITY, na.rm = TRUE),
    IQR = IQR(pop_fit_max  / DIMENSIONALITY, na.rm = TRUE)
  )
```

T 2
```{r tru-exp-mvc-per-2}
wilcox.test(x = filter(slices, T == 2 & Generation == 50000)$pop_fit_max,
            y = filter(slices, T == 2 & Generation == 40000)$pop_fit_max,
            alternative = 't')
```

T 4
```{r tru-exp-mvc-per-4}
wilcox.test(x = filter(slices, T == 4 & Generation == 50000)$pop_fit_max,
            y = filter(slices, T == 4 & Generation == 40000)$pop_fit_max,
            alternative = 't')
```

T 8
```{r tru-exp-mvc-per-8}
wilcox.test(x = filter(slices, T == 8 & Generation == 50000)$pop_fit_max,
            y = filter(slices, T == 8 & Generation == 40000)$pop_fit_max,
            alternative = 't')
```

T 16
```{r tru-exp-mvc-per-16}
wilcox.test(x = filter(slices, T == 16 & Generation == 50000)$pop_fit_max,
            y = filter(slices, T == 16 & Generation == 40000)$pop_fit_max,
            alternative = 't')
```

T 32
```{r tru-exp-mvc-per-32}
wilcox.test(x = filter(slices, T == 32 & Generation == 50000)$pop_fit_max,
            y = filter(slices, T == 32 & Generation == 40000)$pop_fit_max,
            alternative = 't')
```

T 64
```{r tru-exp-mvc-per-64}
wilcox.test(x = filter(slices, T == 64 & Generation == 50000)$pop_fit_max,
            y = filter(slices, T == 64 & Generation == 40000)$pop_fit_max,
            alternative = 't')
```

T 128
```{r tru-exp-mvc-per-128}
wilcox.test(x = filter(slices, T == 128 & Generation == 50000)$pop_fit_max,
            y = filter(slices, T == 128 & Generation == 40000)$pop_fit_max,
            alternative = 't')
```

T 256
```{r tru-exp-mvc-per-256}
wilcox.test(x = filter(slices, T == 256 & Generation == 50000)$pop_fit_max,
            y = filter(slices, T == 256 & Generation == 40000)$pop_fit_max,
            alternative = 't')
```


## Ordered exploitation results

Here we present the results for **best performances** found by each truncation selection size value replicate on the ordered exploitation diagnostic.
Best performance found refers to the largest average trait score found in a given population.
Note that performance values fall between 0 and 100.

### Performance over time

Performance over time.

```{r tru-ord-per, warning=FALSE}
lines = filter(tru_ot, diagnostic == 'ordered_exploitation') %>%
        group_by(T, gen) %>%
          dplyr::summarise(
            min = min(pop_fit_max),
            mean = mean(pop_fit_max),
            max = max(pop_fit_max)
          )
ggplot(lines, aes(x=gen, y=mean / DIMENSIONALITY, group = T, fill = T, color = T, shape = T)) +
  geom_ribbon(aes(ymin = min / DIMENSIONALITY, ymax = max / DIMENSIONALITY), alpha = 0.1) +
  geom_line(size = 0.5) +
  geom_point(data = filter(lines, gen %% 2000 == 0 & gen != 0), size = 1.5, stroke = 2.0, alpha = 1.0) +
  scale_y_continuous(
    name="Average trait score",
    limits=c(-1, 101),
    breaks=seq(0,100, 20),
    labels=c("0", "20", "40", "60", "80", "100")
  ) +
  scale_x_continuous(
    name="Generations",
    limits=c(0, 50000),
    breaks=c(0, 10000, 20000, 30000, 40000, 50000),
    labels=c("0e+4", "1e+4", "2e+4", "3e+4", "4e+4", "5e+4")

  ) +
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette) +
  scale_fill_manual(values = cb_palette) +
  ggtitle("Best performance over time") +
  p_theme
```

### Generation satisfactory solution found

The first Generations a satisfactory solution is found throughout the 50,000 generations.

```{r tru-ord-ssf}
filter(tru_ssf, Diagnostic == 'ORDERED_EXPLOITATION') %>%
ggplot(., aes(x = T, y = Generations, color = T, fill = T, shape = T)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), scale = 'width', alpha = 0.2) +
  geom_point(position = position_jitter(width = .1), size = 1.5, alpha = 1.0) +
  geom_boxplot(color = 'black', width = .2, outlier.shape = NA, alpha = 0.0) +
  scale_shape_manual(values=SHAPE)+
  scale_y_continuous(
    name="Generation",
    limits=c(0, 60000),
    breaks=c(0, 10000, 20000, 30000, 40000, 50000, 60000),
    labels=c("0e+4", "1e+4", "2e+4", "3e+4", "4e+4", "5e+4", "Fail")
  ) +
  scale_x_discrete(
    name="T"
  ) +
  scale_colour_manual(values = cb_palette) +
  scale_fill_manual(values = cb_palette) +
  ggtitle("Generation satisfactory solution found") +
  p_theme
```

#### Stats

Summary statistics for the first Generations a satisfactory solution is found throughout the 50,000 generations.

```{r tru-ord-ssf-sum}
ssf = filter(tru_ssf, Diagnostic == 'ORDERED_EXPLOITATION')
group_by(ssf, T) %>%
  dplyr::summarise(
    count = n(),
    na_cnt = sum(is.na(Generations)),
    min = min(Generations, na.rm = TRUE),
    median = median(Generations, na.rm = TRUE),
    mean = mean(Generations, na.rm = TRUE),
    max = max(Generations, na.rm = TRUE),
    IQR = IQR(Generations, na.rm = TRUE)
  )
```

Kruskal–Wallis test provides evidence of significant differences among the first Generations a satisfactory solution is found throughout the 50,000 generations.

```{r tru-ord-ssf-kru}
kruskal.test(Generations ~ T, data = ssf)
```

Results for post-hoc Wilcoxon rank-sum test with a Bonferroni correction on the first Generations a satisfactory solution is found throughout the 50,000 generations.

```{r tru-ord-ssf-wil}
pairwise.wilcox.test(x = ssf$Generations, g = ssf$T , p.adjust.method = "bonferroni",
                     paired = FALSE, conf.int = FALSE, alternative = 'g')
```

### Multi-valley crossing

#### Performance over time

```{r tru-ord-mvc-per}
# data for lines and shading on plots
lines = filter(tru_ot_mvc, diagnostic == 'ordered_exploitation') %>%
  group_by(T, gen) %>%
  dplyr::summarise(
    min = min(pop_fit_max) / DIMENSIONALITY,
    mean = mean(pop_fit_max) / DIMENSIONALITY,
    max = max(pop_fit_max) / DIMENSIONALITY
  )

ggplot(lines, aes(x=gen, y=mean, group = T, fill =T, color = T, shape = T)) +
  geom_ribbon(aes(ymin = min, ymax = max), alpha = 0.1) +
  geom_line(size = 0.5) +
  geom_point(data = filter(lines, gen %% 2000 == 0 & gen != 0), size = 1.5, stroke = 2.0, alpha = 1.0) +
  scale_y_continuous(
    name="Average trait score"
  ) +
  scale_x_continuous(
    name="Generations",
    limits=c(0, 50000),
    breaks=c(0, 10000, 20000, 30000, 40000, 50000),
    labels=c("0e+4", "1e+4", "2e+4", "3e+4", "4e+4", "5e+4")

  ) +
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette) +
  scale_fill_manual(values = cb_palette) +
  ggtitle('Performance over time')+
  p_theme +
  guides(
    shape=guide_legend(nrow=2, title.position = "left"),
    color=guide_legend(nrow=2, title.position = "left"),
    fill=guide_legend(nrow=2, title.position = "left")
  )

```

#### Performance comparison

Best performances in the population at 40,000 and 50,000 generations.

```{r tru-ord-mvc-per-sli, warning=FALSE}
# 80% and final generation comparison
end = filter(tru_ot_mvc, diagnostic == 'ordered_exploitation' & gen == 50000 & T != 'ran')
end$Generation <- factor(end$gen)

mid = filter(tru_ot_mvc, diagnostic == 'ordered_exploitation' & gen == 40000 & T != 'ran')
mid$Generation <- factor(mid$gen)

mvc_p = ggplot(mid, aes(x = T, y=pop_fit_max / DIMENSIONALITY, group = T, shape = Generation)) +
  geom_point(col = mvc_col[1] , position = position_jitternudge(jitter.width = .03, nudge.x = -0.05), size = 2, alpha = 1.0) +
  geom_boxplot(position = position_nudge(x = -.15, y = 0), lwd = 0.7, col = mvc_col[1], fill = mvc_col[1], width = .1, outlier.shape = NA, alpha = 0.0) +

  geom_point(data = end, aes(x = T, y=pop_fit_max / DIMENSIONALITY), col = mvc_col[2], position = position_jitternudge(jitter.width = .03, nudge.x = 0.05), size = 2, alpha = 1.0) +
  geom_boxplot(data = end, aes(x = T, y=pop_fit_max / DIMENSIONALITY), position = position_nudge(x = .15, y = 0), lwd = 0.7, col = mvc_col[2], fill = mvc_col[2], width = .1, outlier.shape = NA, alpha = 0.0) +

  scale_y_continuous(
    name="Average trait score"
  ) +
  scale_x_discrete(
    name="T"
  )+
  scale_shape_manual(values=c(0,1))+
  scale_colour_manual(values = c(mvc_col[1],mvc_col[2])) +
  p_theme

plot_grid(
  mvc_p +
    ggtitle("Performance comparisons") +
    theme(legend.position="none"),
  legend,
  nrow=2,
  rel_heights = c(1,.05),
  label_size = TSIZE
)
```

#### Stats

Summary statistics for the performance of the best performance at 40,000 and 50,000 generations.

```{r tru-ord-mvc-per-sli-sum}
slices = filter(tru_ot_mvc, diagnostic == 'ordered_exploitation' & (gen == 50000 | gen == 40000))
slices$Generation <- factor(slices$gen, levels = c(50000,40000))
slices %>%
  group_by(T, Generation) %>%
  dplyr::summarise(
    count = n(),
    na_cnt = sum(is.na(pop_fit_max  / DIMENSIONALITY)),
    min = min(pop_fit_max  / DIMENSIONALITY, na.rm = TRUE),
    median = median(pop_fit_max  / DIMENSIONALITY, na.rm = TRUE),
    mean = mean(pop_fit_max  / DIMENSIONALITY, na.rm = TRUE),
    max = max(pop_fit_max  / DIMENSIONALITY, na.rm = TRUE),
    IQR = IQR(pop_fit_max  / DIMENSIONALITY, na.rm = TRUE)
  )
```

T 2
```{r tru-ord-mvc-per-2}
wilcox.test(x = filter(slices, T == 2 & Generation == 50000)$pop_fit_max,
            y = filter(slices, T == 2 & Generation == 40000)$pop_fit_max,
            alternative = 't')
```

T 4
```{r tru-ord-mvc-per-4}
wilcox.test(x = filter(slices, T == 4 & Generation == 50000)$pop_fit_max,
            y = filter(slices, T == 4 & Generation == 40000)$pop_fit_max,
            alternative = 't')
```

T 8
```{r tru-ord-mvc-per-8}
wilcox.test(x = filter(slices, T == 8 & Generation == 50000)$pop_fit_max,
            y = filter(slices, T == 8 & Generation == 40000)$pop_fit_max,
            alternative = 't')
```

T 16
```{r tru-ord-mvc-per-16}
wilcox.test(x = filter(slices, T == 16 & Generation == 50000)$pop_fit_max,
            y = filter(slices, T == 16 & Generation == 40000)$pop_fit_max,
            alternative = 't')
```

T 32
```{r tru-ord-mvc-per-32}
wilcox.test(x = filter(slices, T == 32 & Generation == 50000)$pop_fit_max,
            y = filter(slices, T == 32 & Generation == 40000)$pop_fit_max,
            alternative = 't')
```

T 64
```{r tru-ord-mvc-per-64}
wilcox.test(x = filter(slices, T == 64 & Generation == 50000)$pop_fit_max,
            y = filter(slices, T == 64 & Generation == 40000)$pop_fit_max,
            alternative = 't')
```

T 128
```{r tru-ord-mvc-per-128}
wilcox.test(x = filter(slices, T == 128 & Generation == 50000)$pop_fit_max,
            y = filter(slices, T == 128 & Generation == 40000)$pop_fit_max,
            alternative = 't')
```

T 256
```{r tru-ord-mvc-per-256}
wilcox.test(x = filter(slices, T == 256 & Generation == 50000)$pop_fit_max,
            y = filter(slices, T == 256 & Generation == 40000)$pop_fit_max,
            alternative = 't')
```

## Contraditory objectives diagnostic

Here we present the results for **satisfactory trait coverage** and **activation gene coverage** found by each truncation selection size value replicate on the ordered exploitation diagnostic.
Satisfactory trait coverage refers to the count of unique satisfied traits in the population, while activation gene coverage refers to the count of unique activation genes in the population.
Note that both coverage values fall between 0 and 100.

### Satisfactory trait coverage

Satisfactory trait coverage analysis.

#### Coverage over time

Satisfactory trait coverage over time.

```{r tru-con-sat, warning=FALSE}
lines = filter(tru_ot, diagnostic == 'contradictory_objectives') %>%
        group_by(T, gen) %>%
          dplyr::summarise(
            min = min(pop_uni_obj),
            mean = mean(pop_uni_obj),
            max = max(pop_uni_obj)
          )
ggplot(lines, aes(x=gen, y=mean, group = T, fill =T, color = T, shape = T)) +
  geom_ribbon(aes(ymin = min, ymax = max), alpha = 0.1) +
  geom_line(size = 0.5) +
  geom_point(data = filter(lines, gen %% 2000 == 0 & gen != 0), size = 1.5, stroke = 2.0, alpha = 1.0) +
  scale_y_continuous(
    name="Coverage"
  ) +
  scale_x_continuous(
    name="Generations",
    limits=c(0, 50000),
    breaks=c(0, 10000, 20000, 30000, 40000, 50000),
    labels=c("0e+4", "1e+4", "2e+4", "3e+4", "4e+4", "5e+4")

  ) +
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette) +
  scale_fill_manual(values = cb_palette) +
  ggtitle("Satisfactory trait coverage over time") +
  p_theme
```

#### Best coverage throughout

Best satisfactory trait coverage throughout 50,000 generations.

```{r tru-con-sat-bst}
filter(tru_best, col == 'pop_uni_obj' & diagnostic == 'contradictory_objectives') %>%
ggplot(., aes(x = T, y = val, color = T, fill = T, shape = T)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), scale = 'width', alpha = 0.2) +
  geom_point(position = position_jitter(width = .1), size = 1.5, alpha = 1.0) +
  geom_boxplot(color = 'black', width = .2, outlier.shape = NA, alpha = 0.0) +
  scale_y_continuous(
    name="Coverage"
  ) +
  scale_x_discrete(
    name="T"
  )+
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette) +
  scale_fill_manual(values = cb_palette) +
  ggtitle("Best satisfactory trait coverage") +
  p_theme
```

##### Stats

Summary statistics for the best satisfactory trait coverage throughout 50,000 generations.

```{r tru-con-sat-sum}
coverage = filter(tru_best, col == 'pop_uni_obj' & diagnostic == 'contradictory_objectives')
group_by(coverage, T) %>%
  dplyr::summarise(
    count = n(),
    na_cnt = sum(is.na(val)),
    min = min(val, na.rm = TRUE),
    median = median(val, na.rm = TRUE),
    mean = mean(val, na.rm = TRUE),
    max = max(val, na.rm = TRUE),
    IQR = IQR(val, na.rm = TRUE)
  )
```

#### End of 50,000 generations

Satisfactory trait coverage in the population at the end of 50,000 generations.

```{r tru-con-sat-end}
filter(tru_ot, diagnostic == 'contradictory_objectives' & gen == 50000) %>%
ggplot(., aes(x = T, y = pop_uni_obj, color = T, fill = T, shape = T)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), scale = 'width', alpha = 0.2) +
  geom_point(position = position_jitter(width = .1), size = 1.5, alpha = 1.0) +
  geom_boxplot(color = 'black', width = .2, outlier.shape = NA, alpha = 0.0) +
  scale_y_continuous(
    name="Coverage"
  ) +
  scale_x_discrete(
    name="T"
  )+
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette) +
  scale_fill_manual(values = cb_palette) +
  ggtitle("Final satisfactory trait coverage") +
  p_theme
```

##### Stats

Summary statistics for satisfactory trait coverage in the population at the end of 50,000 generations.

```{r tru-con-sat-end-sum}
coverage = filter(tru_ot, diagnostic == 'contradictory_objectives' & gen == 50000)
group_by(coverage, T) %>%
  dplyr::summarise(
    count = n(),
    na_cnt = sum(is.na(pop_uni_obj)),
    min = min(pop_uni_obj, na.rm = TRUE),
    median = median(pop_uni_obj, na.rm = TRUE),
    mean = mean(pop_uni_obj, na.rm = TRUE),
    max = max(pop_uni_obj, na.rm = TRUE),
    IQR = IQR(pop_uni_obj, na.rm = TRUE)
  )
```

### Activation gene coverage

Here we analyze the activation gene coverage for each parameter replicate on the contradictory objectives diagnostic.

#### Coverage over time

Activation gene coverage over time.

```{r tru-con-act, warning=FALSE}
lines = filter(tru_ot, diagnostic == 'contradictory_objectives') %>%
        group_by(T, gen) %>%
          dplyr::summarise(
            min = min(uni_str_pos),
            mean = mean(uni_str_pos),
            max = max(uni_str_pos)
          )
ggplot(lines, aes(x=gen, y=mean, group = T, fill =T, color = T, shape = T)) +
  geom_ribbon(aes(ymin = min, ymax = max), alpha = 0.1) +
  geom_line(size = 0.5) +
  geom_point(data = filter(lines, gen %% 2000 == 0 & gen != 0), size = 1.5, stroke = 2.0, alpha = 1.0) +
  scale_y_continuous(
    name="Coverage",
    limits=c(-1, 101),
    breaks=seq(0,100, 20),
    labels=c("0", "20", "40", "60", "80", "100")
  ) +
  scale_x_continuous(
    name="Generations",
    limits=c(0, 50000),
    breaks=c(0, 10000, 20000, 30000, 40000, 50000),
    labels=c("0e+4", "1e+4", "2e+4", "3e+4", "4e+4", "5e+4")

  ) +
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette) +
  scale_fill_manual(values = cb_palette) +
  ggtitle("Activation gene coverage over time") +
  p_theme
```

#### End of 50,000 generations

Activation gene coverage in the population at the end of 50,000 generations.

```{r tru-con-act-end}
filter(tru_ot, diagnostic == 'contradictory_objectives' & gen == 50000) %>%
ggplot(., aes(x = T, y = uni_str_pos, color = T, fill = T, shape = T)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), scale = 'width', alpha = 0.2) +
  geom_point(position = position_jitter(width = .1), size = 1.5, alpha = 1.0) +
  geom_boxplot(color = 'black', width = .2, outlier.shape = NA, alpha = 0.0) +
  scale_y_continuous(
    name="Coverage"
  ) +
  scale_x_discrete(
    name="T"
  )+
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette) +
  scale_fill_manual(values = cb_palette) +
  ggtitle("Final activation gene coverage") +
  p_theme
```

##### Stats

Summary statistics for activation gene coverage in the population at the end of 50,000 generations.

```{r tru-con-act-end-sum}
coverage = filter(tru_ot, diagnostic == 'contradictory_objectives' & gen == 50000)
group_by(coverage, T) %>%
  dplyr::summarise(
    count = n(),
    na_cnt = sum(is.na(uni_str_pos)),
    min = min(uni_str_pos, na.rm = TRUE),
    median = median(uni_str_pos, na.rm = TRUE),
    mean = mean(uni_str_pos, na.rm = TRUE),
    max = max(uni_str_pos, na.rm = TRUE),
    IQR = IQR(uni_str_pos, na.rm = TRUE)
  )
```

### Multi-valley crossing

#### Satisfactory trait coverage over time

```{r tru-con-mvc-sat-ot}
lines = filter(tru_ot_mvc, diagnostic == 'contradictory_objectives') %>%
  group_by(T, gen) %>%
  dplyr::summarise(
    min = min(pop_uni_obj),
    mean = mean(pop_uni_obj),
    max = max(pop_uni_obj)
  )
ggplot(lines, aes(x=gen, y=mean, group = T, fill =T, color = T, shape = T)) +
  geom_ribbon(aes(ymin = min, ymax = max), alpha = 0.1) +
  geom_line(size = 0.5) +
  geom_point(data = filter(lines, gen %% 2000 == 0 & gen != 0), size = 1.5, stroke = 2.0, alpha = 1.0) +
  scale_y_continuous(
    name="Coverage"
  ) +
  scale_x_continuous(
    name="Generations",
    limits=c(0, 50000),
    breaks=c(0, 10000, 20000, 30000, 40000, 50000),
    labels=c("0e+4", "1e+4", "2e+4", "3e+4", "4e+4", "5e+4")

  ) +
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette) +
  scale_fill_manual(values = cb_palette) +
  ggtitle("Satisfactory trait coverage over time") +
  p_theme
```

#### Satisfactory trait coverage comparison

Best performances in the population at 40,000 and 50,000 generations.

```{r tru-con-mvc-sat-sli, warning=FALSE}
# 80% and final generation comparison
end = filter(tru_ot_mvc, diagnostic == 'contradictory_objectives' & gen == 50000)
end$Generation <- factor(end$gen)

mid = filter(tru_ot_mvc, diagnostic == 'contradictory_objectives' & gen == 40000)
mid$Generation <- factor(mid$gen)

mvc_p = ggplot(mid, aes(x = T, y=pop_uni_obj, group = T, shape = Generation)) +
  geom_point(col = mvc_col[1] , position = position_jitternudge(jitter.width = .03, nudge.x = -0.05), size = 2, alpha = 1.0) +
  geom_boxplot(position = position_nudge(x = -.15, y = 0), lwd = 0.7, col = mvc_col[1], fill = mvc_col[1], width = .1, outlier.shape = NA, alpha = 0.0) +

  geom_point(data = end, aes(x = T, y=pop_uni_obj), col = mvc_col[2], position = position_jitternudge(jitter.width = .03, nudge.x = 0.05), size = 2, alpha = 1.0) +
  geom_boxplot(data = end, aes(x = T, y=pop_uni_obj), position = position_nudge(x = .15, y = 0), lwd = 0.7, col = mvc_col[2], fill = mvc_col[2], width = .1, outlier.shape = NA, alpha = 0.0) +

  scale_y_continuous(
    name="Coverage",
  ) +
  scale_x_discrete(
    name="T"
  )+
  scale_shape_manual(values=c(0,1))+
  scale_colour_manual(values = c(mvc_col[1],mvc_col[2])) +
  p_theme

plot_grid(
  mvc_p +
    ggtitle("Satisfactory trait coverage") +
    theme(legend.position="none"),
  legend,
  nrow=2,
  rel_heights = c(1,.05),
  label_size = TSIZE
)
```

##### Stats

Summary statistics for the performance of the best performance at 40,000 and 50,000 generations.

```{r tru-con-mvc-sat-sli-sum}
slices = filter(tru_ot_mvc, diagnostic == 'contradictory_objectives' & (gen == 50000 | gen == 40000))
slices$Generation <- factor(slices$gen, levels = c(50000,40000))
slices %>%
  group_by(T, Generation) %>%
  dplyr::summarise(
    count = n(),
    na_cnt = sum(is.na(pop_uni_obj)),
    min = min(pop_uni_obj, na.rm = TRUE),
    median = median(pop_uni_obj, na.rm = TRUE),
    mean = mean(pop_uni_obj, na.rm = TRUE),
    max = max(pop_uni_obj, na.rm = TRUE),
    IQR = IQR(pop_uni_obj, na.rm = TRUE)
  )
```

T 2
```{r tru-con-mvc-sat-2}
wilcox.test(x = filter(slices, T == 2 & Generation == 50000)$pop_uni_obj,
            y = filter(slices, T == 2 & Generation == 40000)$pop_uni_obj,
            alternative = 't')
```

T 4
```{r tru-con-mvc-sat-4}
wilcox.test(x = filter(slices, T == 4 & Generation == 50000)$pop_uni_obj,
            y = filter(slices, T == 4 & Generation == 40000)$pop_uni_obj,
            alternative = 't')
```

T 8
```{r tru-con-mvc-sat-8}
wilcox.test(x = filter(slices, T == 8 & Generation == 50000)$pop_uni_obj,
            y = filter(slices, T == 8 & Generation == 40000)$pop_uni_obj,
            alternative = 't')
```

T 16
```{r tru-con-mvc-sat-16}
wilcox.test(x = filter(slices, T == 16 & Generation == 50000)$pop_uni_obj,
            y = filter(slices, T == 16 & Generation == 40000)$pop_uni_obj,
            alternative = 't')
```

T 32
```{r tru-con-mvc-sat-32}
wilcox.test(x = filter(slices, T == 32 & Generation == 50000)$pop_uni_obj,
            y = filter(slices, T == 32 & Generation == 40000)$pop_uni_obj,
            alternative = 't')
```

T 64
```{r tru-con-mvc-sat-64}
wilcox.test(x = filter(slices, T == 64 & Generation == 50000)$pop_uni_obj,
            y = filter(slices, T == 64 & Generation == 40000)$pop_uni_obj,
            alternative = 't')
```

T 128
```{r tru-con-mvc-sat-128}
wilcox.test(x = filter(slices, T == 128 & Generation == 50000)$pop_uni_obj,
            y = filter(slices, T == 128 & Generation == 40000)$pop_uni_obj,
            alternative = 't')
```

T 256
```{r tru-con-mvc-sat-256}
wilcox.test(x = filter(slices, T == 256 & Generation == 50000)$pop_uni_obj,
            y = filter(slices, T == 256 & Generation == 40000)$pop_uni_obj,
            alternative = 't')
```


#### Activation gene coverage over time

```{r tru-con-mvc-act-ot}
lines = filter(tru_ot_mvc, diagnostic == 'contradictory_objectives') %>%
  group_by(T, gen) %>%
  dplyr::summarise(
    min = min(uni_str_pos),
    mean = mean(uni_str_pos),
    max = max(uni_str_pos)
  )
ggplot(lines, aes(x=gen, y=mean, group = T, fill =T, color = T, shape = T)) +
  geom_ribbon(aes(ymin = min, ymax = max), alpha = 0.1) +
  geom_line(size = 0.5) +
  geom_point(data = filter(lines, gen %% 2000 == 0 & gen != 0), size = 1.5, stroke = 2.0, alpha = 1.0) +
  scale_y_continuous(
    name="Coverage"
  ) +
  scale_x_continuous(
    name="Generations",
    limits=c(0, 50000),
    breaks=c(0, 10000, 20000, 30000, 40000, 50000),
    labels=c("0e+4", "1e+4", "2e+4", "3e+4", "4e+4", "5e+4")

  ) +
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette) +
  scale_fill_manual(values = cb_palette) +
  ggtitle("Activation gene coverage over time") +
  p_theme
```

#### Activation gene coverage comparison

Activation gene coverage in the population at 40,000 and 50,000 generations.

```{r tru-con-mvc-act-sli, warning=FALSE}
# 80% and final generation comparison
end = filter(tru_ot_mvc, diagnostic == 'contradictory_objectives' & gen == 50000)
end$Generation <- factor(end$gen)

mid = filter(tru_ot_mvc, diagnostic == 'contradictory_objectives' & gen == 40000)
mid$Generation <- factor(mid$gen)

mvc_p = ggplot(mid, aes(x = T, y=uni_str_pos, group = T, shape = Generation)) +
  geom_point(col = mvc_col[1] , position = position_jitternudge(jitter.width = .03, nudge.x = -0.05), size = 2, alpha = 1.0) +
  geom_boxplot(position = position_nudge(x = -.15, y = 0), lwd = 0.7, col = mvc_col[1], fill = mvc_col[1], width = .1, outlier.shape = NA, alpha = 0.0) +

  geom_point(data = end, aes(x = T, y=uni_str_pos), col = mvc_col[2], position = position_jitternudge(jitter.width = .03, nudge.x = 0.05), size = 2, alpha = 1.0) +
  geom_boxplot(data = end, aes(x = T, y=uni_str_pos), position = position_nudge(x = .15, y = 0), lwd = 0.7, col = mvc_col[2], fill = mvc_col[2], width = .1, outlier.shape = NA, alpha = 0.0) +

  scale_y_continuous(
    name="Coverage",
  ) +
  scale_x_discrete(
    name="T"
  )+
  scale_shape_manual(values=c(0,1))+
  scale_colour_manual(values = c(mvc_col[1],mvc_col[2])) +
  p_theme

plot_grid(
  mvc_p +
    ggtitle("Activation gene coverage") +
    theme(legend.position="none"),
  legend,
  nrow=2,
  rel_heights = c(1,.05),
  label_size = TSIZE
)
```

##### Stats

Summary statistics for the activation gene coverage at 40,000 and 50,000 generations.

```{r tru-con-mvc-act-sli-sum}
slices = filter(tru_ot_mvc, diagnostic == 'contradictory_objectives' & (gen == 50000 | gen == 40000))
slices$Generation <- factor(slices$gen, levels = c(50000,40000))
slices %>%
  group_by(T, Generation) %>%
  dplyr::summarise(
    count = n(),
    na_cnt = sum(is.na(uni_str_pos)),
    min = min(uni_str_pos, na.rm = TRUE),
    median = median(uni_str_pos, na.rm = TRUE),
    mean = mean(uni_str_pos, na.rm = TRUE),
    max = max(uni_str_pos, na.rm = TRUE),
    IQR = IQR(uni_str_pos, na.rm = TRUE)
  )

```

T 2
```{r tru-con-mvc-act-2}
wilcox.test(x = filter(slices, T == 2 & Generation == 50000)$uni_str_pos,
            y = filter(slices, T == 2 & Generation == 40000)$uni_str_pos,
            alternative = 't')
```

T 4
```{r tru-con-mvc-act-4}
wilcox.test(x = filter(slices, T == 4 & Generation == 50000)$uni_str_pos,
            y = filter(slices, T == 4 & Generation == 40000)$uni_str_pos,
            alternative = 't')
```

T 8
```{r tru-con-mvc-act-8}
wilcox.test(x = filter(slices, T == 8 & Generation == 50000)$uni_str_pos,
            y = filter(slices, T == 8 & Generation == 40000)$uni_str_pos,
            alternative = 't')
```

T 16
```{r tru-con-mvc-act-16}
wilcox.test(x = filter(slices, T == 16 & Generation == 50000)$uni_str_pos,
            y = filter(slices, T == 16 & Generation == 40000)$uni_str_pos,
            alternative = 't')
```

T 32
```{r tru-con-mvc-act-32}
wilcox.test(x = filter(slices, T == 32 & Generation == 50000)$uni_str_pos,
            y = filter(slices, T == 32 & Generation == 40000)$uni_str_pos,
            alternative = 't')
```

T 64
```{r tru-con-mvc-act-64}
wilcox.test(x = filter(slices, T == 64 & Generation == 50000)$uni_str_pos,
            y = filter(slices, T == 64 & Generation == 40000)$uni_str_pos,
            alternative = 't')
```

T 128
```{r tru-con-mvc-act-128}
wilcox.test(x = filter(slices, T == 128 & Generation == 50000)$uni_str_pos,
            y = filter(slices, T == 128 & Generation == 40000)$uni_str_pos,
            alternative = 't')
```

T 256
```{r tru-con-mvc-act-256}
wilcox.test(x = filter(slices, T == 256 & Generation == 50000)$uni_str_pos,
            y = filter(slices, T == 256 & Generation == 40000)$uni_str_pos,
            alternative = 't')
```

## Multi-path exploration results

Here we present the results for **best performances** and **activation gene coverage** found by each truncation selection size value replicate on the multi-path exploration diagnostic.
Best performance found refers to the largest average trait score found in a given population, while activation gene coverage refers to the count of unique activation genes in the population.
Note that both values fall between 0 and 100.

### Performance

Here we analyze the performances for each parameter replicate on the multi-path exploration diagnostic.

#### Performance over time

Performance over time.

```{r tru-mpe-per, warning=FALSE}
lines = filter(tru_ot, diagnostic == 'multipath_exploration') %>%
        group_by(T, gen) %>%
          dplyr::summarise(
            min = min(pop_fit_max),
            mean = mean(pop_fit_max),
            max = max(pop_fit_max)
          )
ggplot(lines, aes(x=gen, y=mean / DIMENSIONALITY, group = T, fill = T, color = T, shape = T)) +
  geom_ribbon(aes(ymin = min / DIMENSIONALITY, ymax = max / DIMENSIONALITY), alpha = 0.1) +
  geom_line(size = 0.5) +
  geom_point(data = filter(lines, gen %% 2000 == 0 & gen != 0), size = 1.5, stroke = 2.0, alpha = 1.0) +
  scale_y_continuous(
    name="Average trait score",
    limits=c(-1, 101),
    breaks=seq(0,100, 20),
    labels=c("0", "20", "40", "60", "80", "100")
  ) +
  scale_x_continuous(
    name="Generations",
    limits=c(0, 50000),
    breaks=c(0, 10000, 20000, 30000, 40000, 50000),
    labels=c("0e+4", "1e+4", "2e+4", "3e+4", "4e+4", "5e+4")

  ) +
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette) +
  scale_fill_manual(values = cb_palette) +
  ggtitle("Best performance over time") +
  p_theme
```

#### Best performance throughout

Here we plot the performance of the best performing solution found throughout 50,000 generations.

```{r tru-mpe-per-bst}
filter(tru_best, col == 'pop_fit_max' & diagnostic == 'multipath_exploration') %>%
ggplot(., aes(x = T, y = val / DIMENSIONALITY, color = T, fill = T, shape = T)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), scale = 'width', alpha = 0.2) +
  geom_point(position = position_jitter(width = .1), size = 1.5, alpha = 1.0) +
  geom_boxplot(color = 'black', width = .2, outlier.shape = NA, alpha = 0.0) +
  scale_y_continuous(
    name="Average trait score",
    limits=c(-1, 101),
    breaks=seq(0,100, 20),
    labels=c("0", "20", "40", "60", "80", "100")
  ) +
  scale_x_discrete(
    name="T"
  )+
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette) +
  scale_fill_manual(values = cb_palette) +
  ggtitle("Best performance throughout") +
  p_theme
```

##### Stats

Summary statistics for the performance of the best performing solution found throughout 50,000 generations.

```{r tru-mpe-per-bst-sum}
performance = filter(tru_best, col == 'pop_fit_max' & diagnostic == 'multipath_exploration')
group_by(performance, T) %>%
  dplyr::summarise(
    count = n(),
    na_cnt = sum(is.na(val)),
    min = min(val / DIMENSIONALITY, na.rm = TRUE),
    median = median(val / DIMENSIONALITY, na.rm = TRUE),
    mean = mean(val / DIMENSIONALITY, na.rm = TRUE),
    max = max(val / DIMENSIONALITY, na.rm = TRUE),
    IQR = IQR(val / DIMENSIONALITY, na.rm = TRUE)
  )
```

Kruskal–Wallis test provides evidence of no statistical differences among the best performing solution found throughout 50,000 generations.

```{r tru-mpe-per-bst-kru}
kruskal.test(val ~ T,data = performance)
```

#### End of 50,000 generations

Best performance in the population at the end of 50,000 generations.

```{r tru-mpe-per-end}
filter(tru_ot, diagnostic == 'multipath_exploration' & gen == 50000) %>%
ggplot(., aes(x = T, y = pop_fit_max / DIMENSIONALITY, color = T, fill = T, shape = T)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), scale = 'width', alpha = 0.2) +
  geom_point(position = position_jitter(width = .1), size = 1.5, alpha = 1.0) +
  geom_boxplot(color = 'black', width = .2, outlier.shape = NA, alpha = 0.0) +
  scale_y_continuous(
    name="Average trait score",
    limits=c(-1, 101),
    breaks=seq(0,100, 20),
    labels=c("0", "20", "40", "60", "80", "100")
  ) +
  scale_x_discrete(
    name="T"
  )+
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette) +
  scale_fill_manual(values = cb_palette) +
  ggtitle("Final performance") +
  p_theme
```

##### Stats

Summary statistics for the best performance in the population at the end of 50,000 generations.

```{r tru-mpe-per-end-sum}
performance = filter(tru_ot, diagnostic == 'multipath_exploration' & gen == 50000)
group_by(performance, T) %>%
  dplyr::summarise(
    count = n(),
    na_cnt = sum(is.na(pop_fit_max / DIMENSIONALITY)),
    min = min(pop_fit_max / DIMENSIONALITY, na.rm = TRUE),
    median = median(pop_fit_max / DIMENSIONALITY, na.rm = TRUE),
    mean = mean(pop_fit_max / DIMENSIONALITY, na.rm = TRUE),
    max = max(pop_fit_max / DIMENSIONALITY, na.rm = TRUE),
    IQR = IQR(pop_fit_max / DIMENSIONALITY, na.rm = TRUE)
  )
```

Kruskal–Wallis test provides evidence of no statistical differences among best performance in the population at the end of 50,000 generations.

```{r tru-mpe-per-end-kru}
kruskal.test(pop_fit_max ~ T, data = performance)
```


### Activation gene coverage

Here we analyze the activation gene coverage for each parameter replicate on the multi-path exploration diagnostic.

#### Coverage over time

Activation gene coverage over time.

```{r tru-mpe-act, warning=FALSE}
lines = filter(tru_ot, diagnostic == 'multipath_exploration') %>%
        group_by(T, gen) %>%
          dplyr::summarise(
            min = min(uni_str_pos),
            mean = mean(uni_str_pos),
            max = max(uni_str_pos)
          )
ggplot(lines, aes(x=gen, y=mean, group = T, fill =T, color = T, shape = T)) +
  geom_ribbon(aes(ymin = min, ymax = max), alpha = 0.1) +
  geom_line(size = 0.5) +
  geom_point(data = filter(lines, gen %% 2000 == 0 & gen != 0), size = 1.5, stroke = 2.0, alpha = 1.0) +
  scale_y_continuous(
    name="Coverage",
    limits=c(-1, 101),
    breaks=seq(0,100, 20),
    labels=c("0", "20", "40", "60", "80", "100")
  ) +
  scale_x_continuous(
    name="Generations",
    limits=c(0, 50000),
    breaks=c(0, 10000, 20000, 30000, 40000, 50000),
    labels=c("0e+4", "1e+4", "2e+4", "3e+4", "4e+4", "5e+4")

  ) +
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette) +
  scale_fill_manual(values = cb_palette) +
  ggtitle("Activation gene coverage over time") +
  p_theme
```

#### End of 50,000 generations

Activation gene coverage in the population at the end of 50,000 generations.

```{r tru-mpe-act-end}
filter(tru_ot, diagnostic == 'multipath_exploration' & gen == 50000) %>%
ggplot(., aes(x = T, y = uni_str_pos, color = T, fill = T, shape = T)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), scale = 'width', alpha = 0.2) +
  geom_point(position = position_jitter(width = .1), size = 1.5, alpha = 1.0) +
  geom_boxplot(color = 'black', width = .2, outlier.shape = NA, alpha = 0.0) +
  scale_y_continuous(
    name="Coverage"
  ) +
  scale_x_discrete(
    name="T"
  )+
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette) +
  scale_fill_manual(values = cb_palette) +
  ggtitle("Final activation gene coverage") +
  p_theme
```

##### Stats

Summary statistics for the activation gene coverage in the population at the end of 50,000 generations.

```{r tru-mpe-act-end-sum}
coverage = filter(tru_ot, diagnostic == 'multipath_exploration' & gen == 50000)
group_by(coverage, T) %>%
  dplyr::summarise(
    count = n(),
    na_cnt = sum(is.na(uni_str_pos)),
    min = min(uni_str_pos, na.rm = TRUE),
    median = median(uni_str_pos, na.rm = TRUE),
    mean = mean(uni_str_pos, na.rm = TRUE),
    max = max(uni_str_pos, na.rm = TRUE),
    IQR = IQR(uni_str_pos, na.rm = TRUE)
  )
```

Kruskal–Wallis test provides evidence of statistical differences among activation gene coverage in the population at the end of 50,000 generations.

```{r tru-mpe-act-end-kru}
kruskal.test(uni_str_pos ~ T, data = coverage)
```

Results for post-hoc Wilcoxon rank-sum test with a Bonferroni correction on the activation gene coverage in the population at the end of 50,000 generations.

```{r tru-mpe-act-end-wil}
pairwise.wilcox.test(x = coverage$uni_str_pos, g = coverage$T , p.adjust.method = "bonferroni",
                     paired = FALSE, conf.int = FALSE, alternative = 't')
```

### Multi-valley crossing

#### Performance over time

```{r tru-mpe-mvc-per}
# data for lines and shading on plots
lines = filter(tru_ot_mvc, diagnostic == 'multipath_exploration') %>%
  group_by(T, gen) %>%
  dplyr::summarise(
    min = min(pop_fit_max) / DIMENSIONALITY,
    mean = mean(pop_fit_max) / DIMENSIONALITY,
    max = max(pop_fit_max) / DIMENSIONALITY
  )

ggplot(lines, aes(x=gen, y=mean, group = T, fill =T, color = T, shape = T)) +
  geom_ribbon(aes(ymin = min, ymax = max), alpha = 0.1) +
  geom_line(size = 0.5) +
  geom_point(data = filter(lines, gen %% 2000 == 0 & gen != 0), size = 1.5, stroke = 2.0, alpha = 1.0) +
  scale_y_continuous(
    name="Average trait score"
  ) +
  scale_x_continuous(
    name="Generations",
    limits=c(0, 50000),
    breaks=c(0, 10000, 20000, 30000, 40000, 50000),
    labels=c("0e+4", "1e+4", "2e+4", "3e+4", "4e+4", "5e+4")

  ) +
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette) +
  scale_fill_manual(values = cb_palette) +
  ggtitle('Performance over time')+
  p_theme +
  guides(
    shape=guide_legend(nrow=2, title.position = "left"),
    color=guide_legend(nrow=2, title.position = "left"),
    fill=guide_legend(nrow=2, title.position = "left")
  )

```

#### Performance comparison

Best performances in the population at 40,000 and 50,000 generations.

```{r tru-mpe-mvc-per-sli, warning=FALSE}
# 80% and final generation comparison
end = filter(tru_ot_mvc, diagnostic == 'multipath_exploration' & gen == 50000 & T != 'ran')
end$Generation <- factor(end$gen)

mid = filter(tru_ot_mvc, diagnostic == 'multipath_exploration' & gen == 40000 & T != 'ran')
mid$Generation <- factor(mid$gen)

mvc_p = ggplot(mid, aes(x = T, y=pop_fit_max / DIMENSIONALITY, group = T, shape = Generation)) +
  geom_point(col = mvc_col[1] , position = position_jitternudge(jitter.width = .03, nudge.x = -0.05), size = 2, alpha = 1.0) +
  geom_boxplot(position = position_nudge(x = -.15, y = 0), lwd = 0.7, col = mvc_col[1], fill = mvc_col[1], width = .1, outlier.shape = NA, alpha = 0.0) +

  geom_point(data = end, aes(x = T, y=pop_fit_max / DIMENSIONALITY), col = mvc_col[2], position = position_jitternudge(jitter.width = .03, nudge.x = 0.05), size = 2, alpha = 1.0) +
  geom_boxplot(data = end, aes(x = T, y=pop_fit_max / DIMENSIONALITY), position = position_nudge(x = .15, y = 0), lwd = 0.7, col = mvc_col[2], fill = mvc_col[2], width = .1, outlier.shape = NA, alpha = 0.0) +

  scale_y_continuous(
    name="Average trait score"
  ) +
  scale_x_discrete(
    name="T"
  )+
  scale_shape_manual(values=c(0,1))+
  scale_colour_manual(values = c(mvc_col[1],mvc_col[2])) +
  p_theme

plot_grid(
  mvc_p +
    ggtitle("Performance comparisons") +
    theme(legend.position="none"),
  legend,
  nrow=2,
  rel_heights = c(1,.05),
  label_size = TSIZE
)
```

#### Stats

Summary statistics for the performance of the best performance at 40,000 and 50,000 generations.

```{r tru-mpe-mvc-per-sli-sum}
slices = filter(tru_ot_mvc, diagnostic == 'multipath_exploration' & (gen == 50000 | gen == 40000))
slices$Generation <- factor(slices$gen, levels = c(50000,40000))
slices %>%
  group_by(T, Generation) %>%
  dplyr::summarise(
    count = n(),
    na_cnt = sum(is.na(pop_fit_max  / DIMENSIONALITY)),
    min = min(pop_fit_max  / DIMENSIONALITY, na.rm = TRUE),
    median = median(pop_fit_max  / DIMENSIONALITY, na.rm = TRUE),
    mean = mean(pop_fit_max  / DIMENSIONALITY, na.rm = TRUE),
    max = max(pop_fit_max  / DIMENSIONALITY, na.rm = TRUE),
    IQR = IQR(pop_fit_max  / DIMENSIONALITY, na.rm = TRUE)
  )
```

T 2
```{r tru-mpe-mvc-per-2}
wilcox.test(x = filter(slices, T == 2 & Generation == 50000)$pop_fit_max,
            y = filter(slices, T == 2 & Generation == 40000)$pop_fit_max,
            alternative = 't')
```

T 4
```{r tru-mpe-mvc-per-4}
wilcox.test(x = filter(slices, T == 4 & Generation == 50000)$pop_fit_max,
            y = filter(slices, T == 4 & Generation == 40000)$pop_fit_max,
            alternative = 't')
```

T 8
```{r tru-mpe-mvc-per-8}
wilcox.test(x = filter(slices, T == 8 & Generation == 50000)$pop_fit_max,
            y = filter(slices, T == 8 & Generation == 40000)$pop_fit_max,
            alternative = 't')
```

T 16
```{r tru-mpe-mvc-per-16}
wilcox.test(x = filter(slices, T == 16 & Generation == 50000)$pop_fit_max,
            y = filter(slices, T == 16 & Generation == 40000)$pop_fit_max,
            alternative = 't')
```

T 32
```{r tru-mpe-mvc-per-32}
wilcox.test(x = filter(slices, T == 32 & Generation == 50000)$pop_fit_max,
            y = filter(slices, T == 32 & Generation == 40000)$pop_fit_max,
            alternative = 't')
```

T 64
```{r tru-mpe-mvc-per-64}
wilcox.test(x = filter(slices, T == 64 & Generation == 50000)$pop_fit_max,
            y = filter(slices, T == 64 & Generation == 40000)$pop_fit_max,
            alternative = 't')
```

T 128
```{r tru-mpe-mvc-per-128}
wilcox.test(x = filter(slices, T == 128 & Generation == 50000)$pop_fit_max,
            y = filter(slices, T == 128 & Generation == 40000)$pop_fit_max,
            alternative = 't')
```

T 256
```{r tru-mpe-mvc-per-256}
wilcox.test(x = filter(slices, T == 256 & Generation == 50000)$pop_fit_max,
            y = filter(slices, T == 256 & Generation == 40000)$pop_fit_max,
            alternative = 't')
```

#### Activation gene coverage over time

```{r tru-mpe-mvc-act-ot}
lines = filter(tru_ot_mvc, diagnostic == 'multipath_exploration') %>%
  group_by(T, gen) %>%
  dplyr::summarise(
    min = min(uni_str_pos),
    mean = mean(uni_str_pos),
    max = max(uni_str_pos)
  )
ggplot(lines, aes(x=gen, y=mean, group = T, fill =T, color = T, shape = T)) +
  geom_ribbon(aes(ymin = min, ymax = max), alpha = 0.1) +
  geom_line(size = 0.5) +
  geom_point(data = filter(lines, gen %% 2000 == 0 & gen != 0), size = 1.5, stroke = 2.0, alpha = 1.0) +
  scale_y_continuous(
    name="Coverage"
  ) +
  scale_x_continuous(
    name="Generations",
    limits=c(0, 50000),
    breaks=c(0, 10000, 20000, 30000, 40000, 50000),
    labels=c("0e+4", "1e+4", "2e+4", "3e+4", "4e+4", "5e+4")

  ) +
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette) +
  scale_fill_manual(values = cb_palette) +
  ggtitle("Activation gene coverage over time") +
  p_theme
```

#### Activation gene coverage comparison

Activation gene coverage in the population at 40,000 and 50,000 generations.

```{r tru-mpe-mvc-act-sli, warning=FALSE}
# 80% and final generation comparison
end = filter(tru_ot_mvc, diagnostic == 'multipath_exploration' & gen == 50000)
end$Generation <- factor(end$gen)

mid = filter(tru_ot_mvc, diagnostic == 'multipath_exploration' & gen == 40000)
mid$Generation <- factor(mid$gen)

mvc_p = ggplot(mid, aes(x = T, y=uni_str_pos, group = T, shape = Generation)) +
  geom_point(col = mvc_col[1] , position = position_jitternudge(jitter.width = .03, nudge.x = -0.05), size = 2, alpha = 1.0) +
  geom_boxplot(position = position_nudge(x = -.15, y = 0), lwd = 0.7, col = mvc_col[1], fill = mvc_col[1], width = .1, outlier.shape = NA, alpha = 0.0) +

  geom_point(data = end, aes(x = T, y=uni_str_pos), col = mvc_col[2], position = position_jitternudge(jitter.width = .03, nudge.x = 0.05), size = 2, alpha = 1.0) +
  geom_boxplot(data = end, aes(x = T, y=uni_str_pos), position = position_nudge(x = .15, y = 0), lwd = 0.7, col = mvc_col[2], fill = mvc_col[2], width = .1, outlier.shape = NA, alpha = 0.0) +

  scale_y_continuous(
    name="Coverage",
  ) +
  scale_x_discrete(
    name="T"
  )+
  scale_shape_manual(values=c(0,1))+
  scale_colour_manual(values = c(mvc_col[1],mvc_col[2])) +
  p_theme

plot_grid(
  mvc_p +
    ggtitle("Activation gene coverage") +
    theme(legend.position="none"),
  legend,
  nrow=2,
  rel_heights = c(1,.05),
  label_size = TSIZE
)
```

##### Stats

Summary statistics for the activation gene coverage at 40,000 and 50,000 generations.

```{r tru-mpe-mvc-act-sli-sum}
slices = filter(tru_ot_mvc, diagnostic == 'multipath_exploration' & (gen == 50000 | gen == 40000))
slices$Generation <- factor(slices$gen, levels = c(50000,40000))
slices %>%
  group_by(T, Generation) %>%
  dplyr::summarise(
    count = n(),
    na_cnt = sum(is.na(uni_str_pos)),
    min = min(uni_str_pos, na.rm = TRUE),
    median = median(uni_str_pos, na.rm = TRUE),
    mean = mean(uni_str_pos, na.rm = TRUE),
    max = max(uni_str_pos, na.rm = TRUE),
    IQR = IQR(uni_str_pos, na.rm = TRUE)
  )

```

T 2
```{r tru-mpe-mvc-act-2}
wilcox.test(x = filter(slices, T == 2 & Generation == 50000)$uni_str_pos,
            y = filter(slices, T == 2 & Generation == 40000)$uni_str_pos,
            alternative = 't')
```

T 4
```{r tru-mpe-mvc-act-4}
wilcox.test(x = filter(slices, T == 4 & Generation == 50000)$uni_str_pos,
            y = filter(slices, T == 4 & Generation == 40000)$uni_str_pos,
            alternative = 't')
```

T 8
```{r tru-mpe-mvc-act-8}
wilcox.test(x = filter(slices, T == 8 & Generation == 50000)$uni_str_pos,
            y = filter(slices, T == 8 & Generation == 40000)$uni_str_pos,
            alternative = 't')
```

T 16
```{r tru-mpe-mvc-act-16}
wilcox.test(x = filter(slices, T == 16 & Generation == 50000)$uni_str_pos,
            y = filter(slices, T == 16 & Generation == 40000)$uni_str_pos,
            alternative = 't')
```

T 32
```{r tru-mpe-mvc-act-32}
wilcox.test(x = filter(slices, T == 32 & Generation == 50000)$uni_str_pos,
            y = filter(slices, T == 32 & Generation == 40000)$uni_str_pos,
            alternative = 't')
```

T 64
```{r tru-mpe-mvc-act-64}
wilcox.test(x = filter(slices, T == 64 & Generation == 50000)$uni_str_pos,
            y = filter(slices, T == 64 & Generation == 40000)$uni_str_pos,
            alternative = 't')
```

T 128
```{r tru-mpe-mvc-act-128}
wilcox.test(x = filter(slices, T == 128 & Generation == 50000)$uni_str_pos,
            y = filter(slices, T == 128 & Generation == 40000)$uni_str_pos,
            alternative = 't')
```

T 256
```{r tru-mpe-mvc-act-256}
wilcox.test(x = filter(slices, T == 256 & Generation == 50000)$uni_str_pos,
            y = filter(slices, T == 256 & Generation == 40000)$uni_str_pos,
            alternative = 't')
```
